---
title: "Entities with American Express as a Vendor"
author: "Michael Jensen"
output: html_notebook
---
# Program Description

**Purpose**

Identify the governments that have American Express as a vendor. 

Given the nature of the credit card American Express offers governments, meaning that it is considered a personal credit card rather than a government or business card, there may be a higher risk of fraud. Thus, Auditor Dougall believes that there isn't a good reason for a government to use American Express.

**Input(s)**

```{r}
dsn_aws        <- "transpAWS"
dsn_salesforce <- "Salesforce"
```

**Output(s)**



# Libraries and Data Sources

```{r}
library(odbc)
library(tidyverse)

odbc_aws        <- dbConnect(odbc::odbc(), dsn_aws)
odbc_salesforce <- dbConnect(odbc::odbc(), dsn_salesforce)
rm(dsn_aws, dsn_salesforce)
```

# Function Definitions

## Argument Definitions

```{r, eval=FALSE}

```


# Execution

```{r}
amex_is_vendor <- 
  dbGetQuery(
    odbc_aws,
    "SELECT 
      entity.name AS entity_name,
      vendor.name AS vendor_name,
      entity_id,
      vendor.id AS vendor_id
    FROM vendor
    JOIN entity
    ON vendor.entity_id = entity.id
    WHERE
      LOWER(vendor.name) LIKE '%american express%' OR
      LOWER(vendor.name) LIKE '%amex%'             OR
      LOWER(vendor.name) LIKE '%am-ex%'")

distinct_vendors <- 
  amex_is_vendor %>% 
  distinct(vendor_name)

distinct_entities <- 
  amex_is_vendor %>% 
  distinct(entity_name)
```

# DBMS Disconnection

```{r}
dbDisconnect()
```