---
title: "Browse AWS Transparency Data"
author: "Michael Jensen"
date: "January 2019"
output: html_notebook
---
# Packages, Data Connection, and Input

```{r}
library(lubridate)
library(odbc)
library(scales)
library(tidyverse)

odbc_aws <- dbConnect(odbc::odbc(), "transpAWS")
```

# Code Templates

## Browse Transparency Data

### Entity Table

```{r}
table_entity <- dbGetQuery(odbc_aws, "SELECT id, name FROM entity")
```

```{sql, connection=odbc_aws, output.var="table_entity"}
SELECT id, name
FROM entity
```

```{sql, connection=odbc_aws, output.var="entity_table"}
SELECT 
  name,
  govt_lvl,
  fiscal_period,
  payroll_period
FROM entity
WHERE id = ?t_id
```

### Batch Table

```{sql, connection=odbc_aws, output.var="table_batch"}
SELECT 
  id,
  upload_date,
  processed_date,
  file_record_count,
  file_total_amount,
  begin_txn_date,
  end_txn_date,
  status,
  status_message
FROM batch
WHERE entity_id = ?t_id
AND status IN ('PROCESSED', 'PROCESSING', 'DONTDELETE')
ORDER BY upload_date DESC
```

```{sql, connection=odbc_aws, output.var="batch_table_status_options"}
SELECT DISTINCT status
FROM batch
```

### Transaction Tables

**Remember**

Transactions for the current and previous four fiscal years are stored in the 
transaction table. The remaining years are stored in separate tables (e.g., 
transaction_2009).

```{sql, connection=odbc_aws, output.var="table_transaction"}
SELECT *
FROM transaction
WHERE batch_id IN (
  SELECT id
  FROM batch
  WHERE entity_id = ?t_id)
```

```{sql, connection=odbc_aws, output.var="batch_data"}
SELECT 
  posting_date, amount, fiscal_year, description, type, 
  org1, org2, org3,
  cat1, cat2, cat3,
  fund1, fund2,
  vendor_id, account_number
FROM transaction
WHERE batch_id = ?batch_id
```

Transactions for a specific batch:

```{r}
table_transaction_group <- 
  dbGetQuery(odbc_aws, "SELECT id, name FROM transaction_group")

table_vendor <- 
  dbGetQuery(odbc_aws, "SELECT id, name FROM vendor WHERE entity_id <> 1")

batch_transactions <- 
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT 
            posting_date, amount, fiscal_year, description, type, 
            org1, org2, org3,
            cat1, cat2, cat3,
            fund1, fund2,
            vendor_id, account_number
          FROM transaction
          WHERE batch_id = ", batch_id)) %>% 
  left_join(table_transaction_group, by = c("org1" = "id")) %>% 
    select(-org1) %>% rename(org1 = name) %>% 
  left_join(table_transaction_group, by = c("org2" = "id")) %>% 
    select(-org2) %>% rename(org2 = name) %>% 
  left_join(table_transaction_group, by = c("org3" = "id")) %>% 
    select(-org3) %>% rename(org3 = name) %>% 
  left_join(table_transaction_group, by = c("cat1" = "id")) %>% 
    select(-cat1) %>% rename(cat1 = name) %>% 
  left_join(table_transaction_group, by = c("cat2" = "id")) %>% 
    select(-cat2) %>% rename(cat2 = name) %>% 
  left_join(table_transaction_group, by = c("cat3" = "id")) %>% 
    select(-cat3) %>% rename(cat3 = name) %>% 
  left_join(table_transaction_group, by = c("fund1" = "id")) %>% 
    select(-fund1) %>% rename(fund1 = name) %>% 
  left_join(table_transaction_group, by = c("fund2" = "id")) %>% 
    select(-fund2) %>% rename(fund2 = name) %>% 
  left_join(table_vendor, by = c("vendor_id" = "id")) %>% 
    select(-vendor_id) %>% rename(vendor_name = name)

distinct_batch_transactions <- 
  list(
    org1 = 
      batch_transactions %>% 
      distinct(org1) %>% 
      arrange(org1),

    org2 = 
      batch_transactions %>% 
      distinct(org2) %>% 
      arrange(org2),
    
    org3 = 
      batch_transactions %>% 
      distinct(org3) %>% 
      arrange(org3),
    
    cat1 = 
      batch_transactions %>% 
      distinct(cat1) %>% 
      arrange(cat1),
    
    cat2 = 
      batch_transactions %>% 
      distinct(cat2) %>% 
      arrange(cat2),
    
    cat3 = 
      batch_transactions %>% 
      distinct(cat3) %>% 
      arrange(cat3),
    
    fund1 =
      batch_transactions %>% 
      distinct(fund1) %>% 
      arrange(fund1),
    
    fund2 = 
      batch_transactions %>% 
      distinct(fund2) %>% 
      arrange(fund2),
    
    ucoa =
      batch_transactions %>% 
      distinct(account_number) %>% 
      arrange(account_number))
```

Non-archived transactions for an entity:

```{r}
table_transaction_group <- 
  dbGetQuery(odbc_aws, "SELECT id, name FROM transaction_group")

table_vendor <- 
  dbGetQuery(odbc_aws, "SELECT id, name FROM vendor WHERE entity_id <> 1")

transactions <- 
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT 
            posting_date, amount, fiscal_year, description, type, 
            org1, org2, org3,
            cat1, cat2, cat3,
            fund1, fu nd2,
            vendor_id, account_number
          FROM transaction
          WHERE batch_id IN (
            SELECT id
            FROM batch
            WHERE entity_id = ", t_id, "
            AND status IN ('PROCESSED', 'PROCESSING', 'DONTDELETE'))")) %>% 
  left_join(table_transaction_group, by = c("org1" = "id")) %>% 
    select(-org1) %>% rename(org1 = name) %>% 
  left_join(table_transaction_group, by = c("org2" = "id")) %>% 
    select(-org2) %>% rename(org2 = name) %>% 
  left_join(table_transaction_group, by = c("org3" = "id")) %>% 
    select(-org3) %>% rename(org3 = name) %>% 
  left_join(table_transaction_group, by = c("cat1" = "id")) %>% 
    select(-cat1) %>% rename(cat1 = name) %>% 
  left_join(table_transaction_group, by = c("cat2" = "id")) %>% 
    select(-cat2) %>% rename(cat2 = name) %>% 
  left_join(table_transaction_group, by = c("cat3" = "id")) %>% 
    select(-cat3) %>% rename(cat3 = name) %>% 
  left_join(table_transaction_group, by = c("fund1" = "id")) %>% 
    select(-fund1) %>% rename(fund1 = name) %>% 
  left_join(table_transaction_group, by = c("fund2" = "id")) %>% 
    select(-fund2) %>% rename(fund2 = name) %>% 
  left_join(table_vendor, by = c("vendor_id" = "id")) %>% 
    select(-vendor_id) %>% rename(vendor_name = name)

distinct_transactions <- 
  list(
    org1 = 
      transactions %>% 
      distinct(org1) %>% 
      arrange(org1),

    org2 = 
      transactions %>% 
      distinct(org2) %>% 
      arrange(org2),
    
    org3 = 
      transactions %>% 
      distinct(org3) %>% 
      arrange(org3),
    
    cat1 = 
      transactions %>% 
      distinct(cat1) %>% 
      arrange(cat1),
    
    cat2 = 
      transactions %>% 
      distinct(cat2) %>% 
      arrange(cat2),
    
    cat3 = 
      transactions %>% 
      distinct(cat3) %>% 
      arrange(cat3),
    
    fund1 =
      transactions %>% 
      distinct(fund1) %>% 
      arrange(fund1),
    
    fund2 = 
      transactions %>% 
      distinct(fund2) %>% 
      arrange(fund2),
    
    ucoa =
      transactions %>% 
      distinct(account_number) %>% 
      arrange(account_number))
```

### Transaction Group Table

```{r}
table_transaction_group <-  
  dbGetQuery(odbc_aws, "SELECT id, name FROM transaction_group")
```

```{sql, connection=odbc_aws, output.var="table_transaction_group"}
SELECT id, name
FROM transaction_group
```

### Summary Table

**Remember**

The information in the Summary Table is for summarizing transactions by `org`, `cat`, `fund`, `program`, and `function`. It is not for summarizing data by fiscal year (do that using the Transaction Table).

```{sql, connection=odbc_aws, output.var="table_summary"}
SELECT *
FROM summary
WHERE entity_id = ?t_id
```

### Vendor Table

**Remember**

The Vendor Table contains all vendors uploaded to Transparency, which means that
it contains vendors that have been deleted. The Vendor Summary Table contains 
current information.

```{r}
table_vendor <- 
  dbGetQuery(odbc_aws, "SELECT id, name, entity_id FROM vendor")
```

```{sql, connection=odbc_aws, output.var="table_vendor"}
SELECT *
FROM vendor
WHERE entity_id = ?t_id
```

### Vendor Summary Table

```{r}
table_vendor_summary <- 
  dbGetQuery(
    odbc_aws, 
    "SELECT entity_id, type, fiscal_year, total, vendor_id FROM vendor_summary")
```

```{sql, connection=odbc_aws, output.var="table_vendor_summary"}
SELECT *
FROM vendor_summary
WHERE entity_id = ?t_id
```

## Browse Transparency Metadata

### Table Row Counts

```{sql, connection = odbc_aws, output.var = "count_batch"}
SELECT COUNT(*) FROM batch
```

```{sql, connection = odbc_aws, output.var = "count_entity"}
SELECT COUNT(*)
FROM entity
```

```{sql, connection = odbc_aws, output.var = "count_transactions"}
SELECT COUNT(*) FROM transaction
```

```{sql, connection = odbc_aws, output.var = "count_deleted_batches"}
SELECT COUNT(*) FROM batch WHERE status = 'DELETED'
```

```{sql, connection = odbc_aws, output.var = "count_deleted_transactions"}
SELECT COUNT(*) 
FROM transaction 
WHERE batch_id IN (
  SELECT id
  FROM batch
  WHERE status = 'DELETED')
```

```{r}
count_batch                <- as.numeric(count_batch$`COUNT(*)`)
count_entity               <- as.numeric(count_entity$`COUNT(*)`)
count_transactions         <- as.numeric(count_transactions$`COUNT(*)`)
count_deleted_batches      <- as.numeric(count_deleted_batches$`COUNT(*)`)
count_deleted_transactions <-
  as.numeric(count_deleted_transactions$`COUNT(*)`)
```

### Information Schema Tables

### Table Names and Information

```{sql, connection = odbc_aws, output.var = "info_schema_tables"}
SELECT *
FROM information_schema.tables
```

```{sql, connection=odbc_aws, output.var=transparency_table_names}
SELECT TABLE_NAME
FROM information_schema.tables
WHERE TABLE_SCHEMA = "transparency"
```

### Data Size

```{sql, connection = odbc_aws, output.var = "info_schema_size"}
SELECT table_schema AS 'Database', 
       table_name AS 'Table',
       ROUND(((DATA_LENGTH + INDEX_LENGTH) / 1024 / 1024), 2) AS 'Size in MB'
FROM information_schema.tables
ORDER BY (DATA_LENGTH + INDEX_LENGTH) DESC
```

```{r}
data_size_in_Mb <- round(sum(info_schema_size$`Size in MB`))
```

### Indexes

Create an index (permission to do so is currently denied):

```{sql, connection = odbc_aws}
CREATE INDEX transaction_batchid
ON transaction (batch_id)
```

View indexed variables:

```{sql, connection = odbc_aws, output.var = "indexed_variables"}
SELECT DISTINCT table_name, index_name
FROM information_schema.statistics
WHERE table_schema = 'transparency'
```

```{sql, connection = odbc_aws, output.var = "index_batch"}
SHOW INDEX FROM batch
```

```{sql, connection = odbc_aws, output.var = "index_entity"}
SHOW INDEX FROM entity
```

```{sql, connection = odbc_aws, output.var = "index_transaction"}
SHOW INDEX FROM transaction
```

### R Object Size

```{r}
entity_transactions %>% 
  object.size() %>% 
  print(units = "auto")
```

# Workspace

```{r}
t_id <- 207

batch_id <- 54692
```

# Close

```{r}
dbDisconnect(odbc_aws)
```