---
title: "Federal Highway Administration Data Request"
author: "Michael Jensen"
date: "July 2019"
output: html_notebook
---
# Program Description

**Purpose**

Give UDOT a sample of the transportation-related data in Transparency in order to help them decide whether to use the Transparency data to complete the Form FHWA-536 (Rev.06/2000) data request from the Federal Highway Administration.

**Input(s)**

```{r}
dsn_aws <- "transpAWS"
```

**Output(s)**

* A count of the number of local governments that report transactions with the UCA fields that Kelly Garner (from UDOT) is interested in.
* A sample of datasets that represent what UDOT will find in the Transparency data.

# Libraries and Data Sources

```{r}
library(magrittr)
library(odbc)
library(readxl)
library(splitstackshape)
library(tidyverse)

odbc_aws <- dbConnect(odbc::odbc(), dsn_aws)

rm(dsn_aws)

download.file(
  "http://financialreports.utah.gov/chartofaccounts/ChartofAccountFull.xlsx",
  "ucoa.xlsx",
  mode = "wb")
```

# Function Definitions

## Argument Definitions

```{r, eval=FALSE}
  #   t_id (num): The entity's Transparency ID, as queried from Transparency.
  #   fiscal_year (num): The fiscal year to query.
  #   funct_or_account_code (char): Which portion of the UCA code to evaluate 
  #   (i.e., "funct" for function or "account").
  #   ucoa_transportation (list): The transportation-related UCA fields UDOT
  #     considers useful.
```

## uses_transp_code

```{r}
uses_transp_code <- function(t_id, fiscal_year, funct_or_account_code,
                             ucoa_transportation) {
  # Determine whether an entity uses any of the transportation-related UCA 
  # codes for the given fiscal year.
  #
  # Arguments:
  #   t_id (num): The entity's Transparency ID, as queried from Transparency.
  #   fiscal_year (num): The fiscal year to query.
  #   funct_or_account_code (char): Which portion of the UCA code to evaluate 
  #   (i.e., "funct" for function or "account").
  #   ucoa_transportation (list): The transportation-related UCA fields UDOT
  #     considers useful.
  #
  # Value:
  #   Numeric (1 or 0).
  
  reported_uca <- 
    dbGetQuery(
    odbc_aws,
    paste("
      SELECT DISTINCT account_number
      FROM transaction
      WHERE fiscal_year = ", fiscal_year, "
      AND type IN (1, 2) 
      AND batch_id IN (
        SELECT id
        FROM batch
        WHERE entity_id = ", t_id, "
        AND status IN ('PROCESSED', 'PROCESSING', 'DONTDELETE'))")) %>% 
    filter(nchar(account_number) == 19) # Filter out invalid UCA codes.
  
  if (funct_or_account_code == "funct") {
    
    functions <- 
      reported_uca %>% 
      .[["account_number"]] %>% 
      substr(5, 10) %>% 
      unique()
    
    if (any(functions %in% ucoa_transportation[["funct"]][["NUMBER"]])) {
      1
    } else {
      0
    }
    
  } else if (funct_or_account_code == "account") {
    
    accounts <- 
      reported_uca %>% 
      .[["account_number"]] %>% 
      substr(12, 19) %>% 
      unique()
    
    if (any(accounts %in% ucoa_transportation[["account_rev"]][["NUMBER"]]) ||
        any(accounts %in% ucoa_transportation[["account_exp"]][["NUMBER"]])) {
      1
    } else {
      0
    }
  }
}
```

# Execution

## UCoA

```{r}
ucoa_fund <- 
  read_xlsx("ucoa.xlsx", sheet = excel_sheets("ucoa.xlsx")[[1]])

ucoa_function <- 
  read_xlsx("ucoa.xlsx", sheet = excel_sheets("ucoa.xlsx")[[2]])

ucoa_account <- 
  read_xlsx("ucoa.xlsx", sheet = excel_sheets("ucoa.xlsx")[[3]])

# Some of the code below will become unnecessary after I edit OSA's Uniform
# Chart of Accounts and publish it on the OSA website.

colnames(ucoa_fund)     <- ucoa_fund[2, ]
colnames(ucoa_function) <- c("NUMBER", ucoa_function[1, 2:4])
colnames(ucoa_account)  <- ucoa_account[2, ]

ucoa_fund     <- ucoa_fund %>% slice(-1, -2)
ucoa_function <- ucoa_function %>% slice(-1)
ucoa_account  <- ucoa_account %>% slice(-1, -2)

extra_fund_numbers <- 
  c(202:298, 302:398, 402:448, 452:498, 502:598, 602:698, 702:798) %>% 
  as.character() %>% 
  enframe(name = NULL) %>% 
  rename("NUMBER" = "value") %>% 
  mutate("SHORT DESCRIPTION" = NA, "FULL DESCRIPTION" = NA, "DETAIL" = NA)

ucoa_fund <- 
  ucoa_fund %>% 
  bind_rows(extra_fund_numbers)

ucoa_fund$NUMBER[[1]]     <- "010"
ucoa_fund$NUMBER[[2]]     <- "020"
ucoa_fund$NUMBER[[3]]     <- "030"
ucoa_function$NUMBER[[1]] <- "000000"

ucoa_account_exp <-
  ucoa_account %>% 
  filter(str_detect(NUMBER, "^4"))

ucoa_account_rev <- 
  ucoa_account %>% 
  filter(str_detect(NUMBER, "^3"))

ucoa <-
  list(
    fund        = ucoa_fund,
    funct       = ucoa_function,
    account     = ucoa_account,
    account_exp = ucoa_account_exp,
    account_rev = ucoa_account_rev)

rm(ucoa_fund, ucoa_function, ucoa_account, extra_fund_numbers, ucoa_account_exp,
   ucoa_account_rev)
```

```{r}
ucoa_transportation <- list()

ucoa_transportation[["funct"]] <- 
  ucoa[["funct"]] %>% 
  filter(
    NUMBER == "200403" | # Patrol
    NUMBER == "200406" | # Traffic Control 
    NUMBER == "300500" | # Transportation
    NUMBER == "300501" | # Administration
    NUMBER == "300502" | # Streets and Highways
    NUMBER == "300503" | # Sidewalks and Crosswalks
    NUMBER == "300504" | # Maintenance and Testing
    NUMBER == "300505" | # Street Cleaning
    NUMBER == "300506" | # Engineering, Design, and Studies
    NUMBER == "300507" | # Street Lighting and Traffic Controls
    NUMBER == "300508" | # Bridges, Viaducts, and Grade Separations
    NUMBER == "300509" | # Tunnels
    NUMBER == "300700" | # Mass Transit
    NUMBER == "300701" | # Administration
    NUMBER == "300702" | # Operations
    NUMBER == "500316" | # Parkways and Boulevards
    NUMBER == "500504")  # Education Safety

ucoa_transportation[["account_rev"]] <- 
  ucoa[["account_rev"]] %>% 
  filter(
    NUMBER == "30010307" | # Mass Transit Tax
    NUMBER == "30010308" | # Transportation Tax
    NUMBER == "30010311" | # Motor Fuels Tax
    NUMBER == "30010312" | # Motor Vehicle Rental Tax
    NUMBER == "30020206" | # Street and Curb Permits
    NUMBER == "30020300" | # Motor Vehicle Registrations
    NUMBER == "30030101" | # Operating Grants
    NUMBER == "30030205" | # Class B and C Road Funds
    NUMBER == "30030206" | # Mineral Lease Allotment
    NUMBER == "30040000" | # Charges for Service
    NUMBER == "30040100" | # Fares
    NUMBER == "30040201" | # Impact Fees
    NUMBER == "30040207")  # Tolls

ucoa_transportation[["account_exp"]] <- 
  ucoa[["account_exp"]] %>% 
  filter(
    NUMBER == "40021200" | # Rental of Equipment and Vehicles
    NUMBER == "40050500" | # Material
    NUMBER == "40050501" | # Construction Material
    NUMBER == "40050502" | # Road Repair Material
    NUMBER == "40050503" | # Salt and Sand
    NUMBER == "40050600" | # Repair and Maintenance
    NUMBER == "40050604" | # Other Assets
    NUMBER == "40050900" | # Signage
    NUMBER == "40080300" | # Infrastructure
    NUMBER == "40080400" | # Construction
    NUMBER == "40170100" | # Principal
    NUMBER == "40170200" | # Interest
    NUMBER == "40170300" | # Fees
    NUMBER == "40170400" | # Bond Issuance Costs
    NUMBER == "40170500")  # Refunds
```

## Transparency

### Number of Governments that use UCoA Transportation Codes

```{r}
entities <- 
  dbGetQuery(
    odbc_aws,
    "
    SELECT id, name, govt_lvl
    FROM entity
    WHERE govt_lvl IN (
      SELECT level_key
      FROM government_level
      WHERE level_key NOT IN (
        'K12 EDUCATION', 'HIGHER EDUCATION', 'STATE', 'INDEPENDENT'))") %>% 
  mutate(
    uses_transp_funct_code = map(
                               id,
                               uses_transp_code, 
                               fiscal_year = 2018,
                               funct_or_account_code = "funct",
                               ucoa_transportation),
    uses_transp_account_code = map(
                                id,
                                uses_transp_code, 
                                fiscal_year = 2018,
                                funct_or_account_code = "account",
                                ucoa_transportation)) %>% 
  unnest()

total_funct <- sum(entities$uses_transp_funct_code)
total_account <- sum(entities$uses_transp_account_code)
```

### 2018 Data from Sample Governments

```{r}
entity_table <- 
  dbGetQuery(
    odbc_aws,
    "SELECT id, name, govt_lvl FROM entity")

transaction_group <- 
  dbGetQuery(
    odbc_aws,
    "SELECT id, name FROM transaction_group")
```

Box Elder County: An entity that doesn't use UCoA transportation codes

```{r}
t_id <- 299
  
box_elder_2018_rev <- 
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT 
            amount, 
            account_number AS chart_of_accounts_code, 
            description AS entity_transaction_description, 
            org1, org2, org3,
            cat1, cat2, cat3,
            fund1, fund2
          FROM transaction
          WHERE fiscal_year = 2018
          AND type = 2
          AND batch_id IN (
            SELECT id
            FROM batch
            WHERE entity_id = ", t_id, "
            AND status = 'PROCESSED')")) %>% 
  cSplit(
    splitCols = "chart_of_accounts_code", 
    sep = "-", 
    direction = "wide", 
    type.convert = FALSE) %>% 
  left_join(transaction_group, by = c("org1" = "id")) %>% 
  select(-org1) %>% 
  rename(org1 = name) %>% 
  left_join(transaction_group, by = c("org2" = "id")) %>% 
  select(-org2) %>% 
  rename(org2 = name) %>% 
  left_join(transaction_group, by = c("org3" = "id")) %>% 
  select(-org3) %>% 
  rename(org3 = name) %>% 
  left_join(transaction_group, by = c("cat1" = "id")) %>% 
  select(-cat1) %>% 
  rename(cat1 = name) %>% 
  left_join(transaction_group, by = c("cat2" = "id")) %>% 
  select(-cat2) %>% 
  rename(cat2 = name) %>% 
  left_join(transaction_group, by = c("cat3" = "id")) %>% 
  select(-cat3) %>% 
  rename(cat3 = name) %>% 
  left_join(transaction_group, by = c("fund1" = "id")) %>% 
  select(-fund1) %>% 
  rename(fund1 = name) %>% 
  left_join(transaction_group, by = c("fund2" = "id")) %>% 
  select(-fund2) %>% 
  rename(fund2 = name)

box_elder_2018_exp <- 
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT 
            amount, 
            account_number AS chart_of_accounts_code, 
            description AS entity_transaction_description, 
            org1, org2, org3,
            cat1, cat2, cat3,
            fund1, fund2
          FROM transaction
          WHERE fiscal_year = 2018
          AND type = 1
          AND batch_id IN (
            SELECT id
            FROM batch
            WHERE entity_id = ", t_id, "
            AND status = 'PROCESSED')")) %>% 
  cSplit(
    splitCols = "chart_of_accounts_code", 
    sep = "-", 
    direction = "wide", 
    type.convert = FALSE) %>% 
  left_join(transaction_group, by = c("org1" = "id")) %>% 
  select(-org1) %>% 
  rename(org1 = name) %>% 
  left_join(transaction_group, by = c("org2" = "id")) %>% 
  select(-org2) %>% 
  rename(org2 = name) %>% 
  left_join(transaction_group, by = c("org3" = "id")) %>% 
  select(-org3) %>% 
  rename(org3 = name) %>% 
  left_join(transaction_group, by = c("cat1" = "id")) %>% 
  select(-cat1) %>% 
  rename(cat1 = name) %>% 
  left_join(transaction_group, by = c("cat2" = "id")) %>% 
  select(-cat2) %>% 
  rename(cat2 = name) %>% 
  left_join(transaction_group, by = c("cat3" = "id")) %>% 
  select(-cat3) %>% 
  rename(cat3 = name) %>% 
  left_join(transaction_group, by = c("fund1" = "id")) %>% 
  select(-fund1) %>% 
  rename(fund1 = name) %>% 
  left_join(transaction_group, by = c("fund2" = "id")) %>% 
  select(-fund2) %>% 
  rename(fund2 = name)

write_csv(box_elder_2018_rev, "box_elder_2018_rev.csv")
write_csv(box_elder_2018_exp, "box_elder_2018_exp.csv")
```

Highland City: An entity that uses UCoA transportation codes

```{r}
t_id <- 445
  
highland_2018_rev <- 
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT 
            amount, 
            account_number AS chart_of_accounts_code, 
            description AS entity_transaction_description, 
            org1, org2, org3,
            cat1, cat2, cat3,
            fund1, fund2
          FROM transaction
          WHERE fiscal_year = 2018
          AND type = 2
          AND batch_id IN (
            SELECT id
            FROM batch
            WHERE entity_id = ", t_id, "
            AND status = 'PROCESSED')")) %>% 
  cSplit(
    splitCols = "chart_of_accounts_code", 
    sep = "-", 
    direction = "wide", 
    type.convert = FALSE) %>% 
  left_join(transaction_group, by = c("org1" = "id")) %>% 
  select(-org1) %>% 
  rename(org1 = name) %>% 
  left_join(transaction_group, by = c("org2" = "id")) %>% 
  select(-org2) %>% 
  rename(org2 = name) %>% 
  left_join(transaction_group, by = c("org3" = "id")) %>% 
  select(-org3) %>% 
  rename(org3 = name) %>% 
  left_join(transaction_group, by = c("cat1" = "id")) %>% 
  select(-cat1) %>% 
  rename(cat1 = name) %>% 
  left_join(transaction_group, by = c("cat2" = "id")) %>% 
  select(-cat2) %>% 
  rename(cat2 = name) %>% 
  left_join(transaction_group, by = c("cat3" = "id")) %>% 
  select(-cat3) %>% 
  rename(cat3 = name) %>% 
  left_join(transaction_group, by = c("fund1" = "id")) %>% 
  select(-fund1) %>% 
  rename(fund1 = name) %>% 
  left_join(transaction_group, by = c("fund2" = "id")) %>% 
  select(-fund2) %>% 
  rename(fund2 = name)

highland_2018_exp <- 
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT 
            amount, 
            account_number AS chart_of_accounts_code, 
            description AS entity_transaction_description, 
            org1, org2, org3,
            cat1, cat2, cat3,
            fund1, fund2
          FROM transaction
          WHERE fiscal_year = 2018
          AND type = 1
          AND batch_id IN (
            SELECT id
            FROM batch
            WHERE entity_id = ", t_id, "
            AND status = 'PROCESSED')")) %>% 
  cSplit(
    splitCols = "chart_of_accounts_code", 
    sep = "-", 
    direction = "wide", 
    type.convert = FALSE) %>% 
  left_join(transaction_group, by = c("org1" = "id")) %>% 
  select(-org1) %>% 
  rename(org1 = name) %>% 
  left_join(transaction_group, by = c("org2" = "id")) %>% 
  select(-org2) %>% 
  rename(org2 = name) %>% 
  left_join(transaction_group, by = c("org3" = "id")) %>% 
  select(-org3) %>% 
  rename(org3 = name) %>% 
  left_join(transaction_group, by = c("cat1" = "id")) %>% 
  select(-cat1) %>% 
  rename(cat1 = name) %>% 
  left_join(transaction_group, by = c("cat2" = "id")) %>% 
  select(-cat2) %>% 
  rename(cat2 = name) %>% 
  left_join(transaction_group, by = c("cat3" = "id")) %>% 
  select(-cat3) %>% 
  rename(cat3 = name) %>% 
  left_join(transaction_group, by = c("fund1" = "id")) %>% 
  select(-fund1) %>% 
  rename(fund1 = name) %>% 
  left_join(transaction_group, by = c("fund2" = "id")) %>% 
  select(-fund2) %>% 
  rename(fund2 = name)

write_csv(highland_2018_rev, "highland_2018_rev.csv")
write_csv(highland_2018_exp, "highland_2018_exp.csv")
```

# DBMS Disconnection

```{r}
dbDisconnect(odbc_aws)
```