---
title: "Granite School District Vendor Analysis"
author: "Michael Jensen"
output: html_notebook
---
# Program Description

**Purpose**

Research non-compliant vendor names at the district level.

**Input(s)**

```{r}
dsn_aws <- "transpAWS"
```

**Output(s)**

A .csv file containing


# Libraries and Data Sources

```{r}
library(ggplot2)
library(odbc)
library(tidyverse)

odbc_aws        <- dbConnect(odbc::odbc(), dsn_aws)
rm(dsn_aws)
```

# Function Definitions

## Argument Definitions

```{r, eval=FALSE}

```


# Execution

## Import and Analyze Granite SD's Transaction and Vendor Data

In the LEA chart of accounts, the location code is the second element, composed of a three-character alphanumeric combination. District-level location codes are `011`-`099`, and Granite SD's district location code is `012`.

```{r}
t_id <- 57

trxns <- 
  dbGetQuery(
    odbc_aws,
    paste("
      SELECT type, fiscal_year, amount, name AS vendor_name, account_number
      FROM transaction
      JOIN vendor
      ON transaction.vendor_id = vendor.id
      WHERE batch_id IN (
        SELECT id
        FROM batch
        WHERE entity_id = ", t_id, ")"))

trxns$fiscal_year <- 
  trxns$fiscal_year %>% as.integer()

trxns_clean <- 
  trxns %>%
  filter(
    str_detect(
      .$account_number,
      regex("^[:digit:]{2}-[:alnum:]{3}-[:digit:]{4}-[:digit:]{4}-[:digit:]{3}-[:digit:]{4}$")))

trxns_clean_distinct <- 
  substring(trxns_clean$account_number, 4, 6) %>% 
  unique() %>% 
  enframe(name = NULL)

trxns_dirty <- 
  trxns %>%
  filter(
    !str_detect(
      .$account_number,
      regex("^[:digit:]{2}-[:alnum:]{3}-[:digit:]{4}-[:digit:]{4}-[:digit:]{3}-[:digit:]{4}$")))

trxns_dirty_distinct <- 
  substring(trxns_dirty$account_number, 4, 6) %>% 
  unique() %>% 
  enframe(name = NULL)

trxns <- 
  list(
    trxns = trxns,
    clean = trxns_clean,
    dirty = trxns_dirty,
    clean_distinct = trxns_clean_distinct,
    dirty_distinct = trxns_dirty_distinct)

rm(trxns_clean, trxns_clean_distinct, trxns_dirty, trxns_dirty_distinct)
```

Conclusions:

* The location portion of `account_number` in `trxns_dirty` is valid, which means that I can include the transactions with dirty `account_number` values in my analysis.
* Granite SD's district-level location code is `012`, but Granite also uses `099`. Given that `099` is a valid district-level location code, I'll include it in my analysis.

## Import and Analyze Granite SD's District-level Transaction and Vendor Data

```{r}
trxns$trxns <- 
  trxns$trxns %>% 
  mutate(location_code = substring(.$account_number, 4, 6),
         location_name = 
           if_else(
             location_code %in% c("012", "099"), "District", "School") %>% 
           as_factor())

trxns$annual_totals <- 
  trxns$trxns %>% 
  group_by(location_name, type, fiscal_year) %>% 
  summarize(total = sum(amount))

# ggplot(
#   trxns_district$yearly_summary,
#   aes(x = fiscal_year, y = total, col = as_factor(type))) +
#   geom_line() +
#   xlab("Fiscal Year") +
#   ylab("Total Amount") +
#   labs(color = "Transaction Type")
```

## Vendor Analysis for Expenses

```{r}
trxns$exp_vendors <- 
  trxns$trxns %>% 
  filter(type == 1) %>% 
  distinct(location_name, vendor_name)


```

```{r}
exp_vendors_na <- 
  trxns$trxns %>% 
  filter(type == 1) %>% 
  filter(
    str_detect(
      .$vendor_name, 
      regex("^Not Applicable", ignore_case = TRUE))) %>% 
  group_by(fiscal_year) %>% 
  summarize(not_applicable_count = n())

exp_vendors_np <- 
  trxns$trxns %>% 
  filter(type == 1) %>% 
  filter(
    str_detect(
      .$vendor_name, 
      regex("^Not Provi", ignore_case = TRUE))) %>% 
  group_by(fiscal_year) %>% 
  summarize(not_provided_count = n())

exp_vendors_vendor_id <- 
  trxns$trxns %>% 
  filter(type == 1) %>% 
  filter(
    str_detect(
      .$vendor_name, 
      regex("^SCH Vendor ID", ignore_case = TRUE)) |
    str_detect(
      .$vendor_name, 
      regex("^Vendor ID", ignore_case = TRUE))) %>% 
  group_by(fiscal_year) %>% 
  summarize(vendor_id_count = n())

exp_vendors_summary <- 
  trxns$trxns %>% 
  filter(type == 1) %>% 
  group_by(fiscal_year) %>% 
  summarize(record_count = n()) %>% 
  full_join(exp_vendors_na, by = "fiscal_year") %>% 
  full_join(exp_vendors_np, by = "fiscal_year") %>% 
  full_join(exp_vendors_vendor_id, by = "fiscal_year") %>% 
  mutate(pct_na = 
           (not_applicable_count / record_count) %>% 
           round(digits = 2) * 100,
         pct_np = 
           (not_provided_count / record_count) %>% 
           round(digits = 2) * 100,
         pct_vendor_id = 
           (vendor_id_count / record_count) %>% 
           round(digits = 2) * 100)
```

```{r}
exp_vendors_na_district <- 
  trxns$trxns %>% 
  filter(type == 1 & location_name == "District") %>% 
  filter(
    str_detect(
      .$vendor_name, 
      regex("^Not Applicable", ignore_case = TRUE))) %>% 
  group_by(fiscal_year) %>% 
  summarize(not_applicable_count = n())

exp_vendors_np_district <- 
  trxns$trxns %>% 
  filter(type == 1 & location_name == "District") %>%  
  filter(
    str_detect(
      .$vendor_name, 
      regex("^Not Provi", ignore_case = TRUE))) %>% 
  group_by(fiscal_year) %>% 
  summarize(not_provided_count = n())

exp_vendors_vendor_id_district <- 
  trxns$trxns %>% 
  filter(type == 1 & location_name == "District") %>%  
  filter(
    str_detect(
      .$vendor_name, 
      regex("^SCH Vendor ID", ignore_case = TRUE)) |
    str_detect(
      .$vendor_name, 
      regex("^Vendor ID", ignore_case = TRUE))) %>% 
  group_by(fiscal_year) %>% 
  summarize(vendor_id_count = n())

exp_vendors_summary_district <- 
  trxns$trxns %>% 
  filter(type == 1 & location_name == "District") %>%  
  group_by(fiscal_year) %>% 
  summarize(record_count = n()) %>% 
  full_join(exp_vendors_na_district, by = "fiscal_year") %>% 
  full_join(exp_vendors_np_district, by = "fiscal_year") %>% 
  full_join(exp_vendors_vendor_id_district, by = "fiscal_year") %>% 
  mutate(pct_na = 
           (not_applicable_count / record_count) %>% 
           round(digits = 2) * 100,
         pct_np = 
           (not_provided_count / record_count) %>% 
           round(digits = 2) * 100,
         pct_vendor_id = 
           (vendor_id_count / record_count) %>% 
           round(digits = 2) * 100)

ggplot(
  exp_vendors_summary_district %>% select(fiscal_year, pct_na, pct_vendor_id),
  aes(x = fiscal_year, y = pct_na)) +
  geom_col()

district_summary <- 
  exp_vendors_summary_district %>% 
  select(fiscal_year, pct_na, pct_np, pct_vendor_id) %>% 
  gather(key = "vendor_name", value = "percentage", -fiscal_year)

district_summary_plot <- 
  ggplot(district_summary,
       aes(x = fiscal_year, y = percentage, fill = vendor_name)) +
  geom_col()

district_summary_plot
```


Expense information contains "Not Applicable," "Not Provided," "SCH Vendor ID: ######," and "Vendor ID: ######."

```{r}

  
library(ggplot2)

ggplot(type_1_total_trxns,
       aes(x = fiscal_year, y = record_count)) +
  geom_point() +
  geom_smooth(
    type_1_total_trxns,
    aes(x = fiscal_year, y = not_applicable_count))


```

## Payroll Analysis

```{r}

trxns_district$type_3 <- 
  trxns_district$trxns %>% filter(type == 3)

type_3_vendors <- 
  trxns %>% 
  filter(type == 3) %>% 
  distinct(vendor_name)

type_3_locations <- 
  substring(trxns$account_number, 4, 6) %>% 
  unique() %>% 
  enframe(name = NULL)
```

For district and school-level information, I didn't see any instances of "Not Applicable," "Not Provided," "SCH Vendor ID: ######," or "Vendor ID: ######" reported as an employee name. Vendor names reported for payroll information look good.

```{r, eval=FALSE}
rm(type_3_locations, type_3_vendors)
```

## Revenue Analysis

```{r}

trxns_district$type_2 <- 
  trxns_district$trxns %>% filter(type == 2)


type_2_locations <- 
  trxns %>% 
  filter(type == 2) %>% 
  substring(trxns$account_number, 4, 6) %>% 
  unique() %>% 
  enframe(name = NULL)

type_2_vendors <- 
  trxns %>% 
  filter(type == 2) %>% 
  distinct(vendor_name)

type_2_vendors_distinct   <-
  type_2_vendors %>% 
  distinct(vendor_name) %>% 
  nrow() %>% as.double()
  
type_2_vendors_na <- 
  trxns %>% 
  filter(type == 2) %>% 
  filter(
    str_detect(
      .$vendor_name, 
      regex("^Not A", ignore_case = TRUE))) %>% 
  group_by(fiscal_year) %>% 
  summarize(not_applicable_count = n())

type_2_vendors_np <- 
  trxns %>% 
  filter(type == 2) %>% 
  filter(
    str_detect(
      .$vendor_name, 
      regex("^Not P", ignore_case = TRUE))) %>% 
  group_by(fiscal_year) %>% 
  summarize(not_provided_count = n())

type_2_total_trxns <- 
  trxns %>% 
  filter(type == 2) %>% 
  group_by(fiscal_year) %>% 
  summarize(record_count = n()) %>% 
  full_join(type_2_vendors_na, by = "fiscal_year") %>% 
  full_join(type_2_vendors_np, by = "fiscal_year") %>% 
  mutate(pct_na = 
           (not_applicable_count / record_count) %>% 
           round(digits = 2) * 100,
         pct_np = 
           (not_provided_count / record_count) %>% 
           round(digits = 2) * 100)

library(ggplot2)

type_2_total_trxns$fiscal_year <- 
  as.integer(type_2_total_trxns$fiscal_year) 

ggplot(type_2_total_trxns, 
       aes(x = fiscal_year, 
           y = record_count)) +
  geom_line()
```

For district and school-level information, I didn't see any instances of "SCH Vendor ID: ######," or "Vendor ID: ######" reported as a vendor name.

## To review

```{r}
 %>% 
  filter(substring(.$account_number, 4, 6) %in% c('012', '099'))
  
coa <- 
  dbGetQuery(
    odbc_aws,
    paste("
      SELECT DISTINCT account_number
      FROM transaction
      WHERE batch_id IN (
        SELECT id
        FROM batch
        WHERE entity_id = ", 57, ")"))

coa_complete <- 
  coa %>% 
  filter(
    str_detect(
      coa$account_number,
      regex("^[:digit:]{2}-[:alnum:]{3}-[:digit:]{4}-[:digit:]{4}-[:digit:]{3}-[:digit:]{4}$")))

coa_location <- 
  coa_complete %>% 
  .[["account_number"]] %>% 
  substring(4, 6) %>% 
  unique() %>% 
  tibble::enframe(name = NULL)

vendors <- 
  dbGetQuery(
    odbc_aws,
    paste("
      SELECT name, id AS vendor_id
      FROM vendor
      WHERE entity_id = ", t_id))



distinct_vendors <- 
  district_vendors %>% 
  distinct(name)

na <- 
  district_vendors %>% 
  filter(
    str_detect(
      .$name, 
      regex("^Not A", ignore_case = TRUE))) %>% 
  count(name) %>% 
  .$n %>% 
  as.double()

np <- 
  district_vendors %>% 
  filter(
    str_detect(
      .$name, 
      regex("^Not P", ignore_case = TRUE))) %>% 
  count(name) %>% 
  .$n %>% 
  as.double()

vendor_id <- 
  district_vendors %>% 
  filter(
    str_detect(
      .$name, 
      regex("^Vendor ID", ignore_case = TRUE))) %>% 
  count(name)
```

# DBMS Disconnection

```{r}
dbDisconnect()
```