---
title: "Identify Insufficiently-detailed State of Utah Transactions"
author: "Michael Jensen"
output: html_notebook
---
# Program Description

**Purpose**



**Input(s)**

```{r}
dsn_aws     <- "transpAWS"
dsn_sf      <- "Salesforce"
dsn_statedw <- "StateDW"
```

**Output(s)**



# Libraries and Data Sources

```{r}
library(odbc)
library(tidyverse)

odbc_aws        <- dbConnect(odbc::odbc(), dsn_aws)
odbc_salesforce <- dbConnect(odbc::odbc(), dsn_sf)
odbc_statedw    <- dbConnect(odbc::odbc(), dsn_statedw, password = "DW1234")
rm(dsn_aws, dsn_sf, dsn_statedw)
```

# Function Definitions

## Argument Definitions

```{r, eval=FALSE}

```


# Execution

```{r}
# Type 22 (expenditures) indicates money spent. Type 24 (expenses) indicates money
# out or something that has been expensed (e.g., a depreciation expense).
table_account_type <- 
  dbGetQuery(odbc_statedw, "SELECT * FROM Account_Type")

table_dpt_and_div <- 
  dbGetQuery(
    odbc_statedw,
    "SELECT DISTINCT
      Department_Name, Division_Name
    FROM Department
    LEFT JOIN Division
    ON Department.Department = Division.Department")
```

## Agency Fund - Political Check-off (State Treasurer)

## Agency Fund - UDOT Mineral Lease (Division of Finance)

```{sql, connection=odbc_statedw, output.var=udot_mineral_lease}
SELECT 
  Fiscal_Year_Period,
  Amount,
  Line_Description,
  Vendor_Customer,
  Vendor_Customer_Name,
  Tran_ID
FROM StateDW.dbo.Accounting_Journal
WHERE Department = "810" -- Utah Department of Transportation
AND Division = "8820"    -- DOT Mineral Lease
AND Fund = "2800"        -- (DOT) Transportation Fund Unrestricted
AND Account_Type = "22"  -- Expenditures
AND (
  --Fiscal_Year_Period LIKE "2014%" OR
  --Fiscal_Year_Period LIKE "2015%" OR
  --Fiscal_Year_Period LIKE "2016%" OR
  --Fiscal_Year_Period LIKE "2017%" OR
  Fiscal_Year_Period LIKE "2018%" OR
  Fiscal_Year_Period LIKE "2019%")
```

## Agency Fund - Property Tax Valuation (State Auditor)

## P-Card - State Auditor

```{r}
osa_pcard <- 
  dbGetQuery(
    odbc_statedw,
    "SELECT 
      Amount, Account_Type, Debit_Credit, Fiscal_Year, Fiscal_Period, 
      Budget_Year_Period, Record_Number, Tran_ID, Ref_Doc_ID, Document_ID,
      Check_Number, ZDate, Run_Date_Time, Doc_Record_Date, Invoice_Date,
      Fund, Department, Unit, Division, Object, Revenue_Source, Appropriation,
      Major_Program, Program, Posting_Code, Vendor_Customer_Indicator,
      Vendor_Customer, Vendor_Customer_Name, Posting_Pair_Type, 
      Doc_Function_Code, Document_Type, Accounting_Line_Number, 
      Commodity_Line_Number, Vendor_Line_Number, Document_Version_Number,
      Document_Code, Doc_Department, Line_Description
    FROM Accounting_Journal
    WHERE Department = '090'
    AND Fiscal_Year = '2020'
    AND Account_Type = '22'")
```

```{r}
table_object <- 
  dbGetQuery(
    odbc_statedw,
    "SELECT Object_Name
    FROM Object
    WHERE Object IN ('6185', '6260')"
  )
```

```{r}
sample_line_descriptions <- 
  dbGetQuery(
    odbc_statedw,
    "SELECT DISTINCT Line_Description
    FROM Accounting_Journal
    WHERE Department = '090'
    AND Fiscal_Year = '2020'
    AND Account_Type = '22'")

# The line descriptions are not formatted the same, so extracting the vendor 
# name from this field will require some thought.
```

## P-card - Alpine School District

Auditor Dougall thought that Alpine School District had solved the problem we are attempting to solve with the State of Utah.

```{r}
t_id <- 259

table_transaction_group <- 
  dbGetQuery(odbc_aws, "SELECT id, name FROM transaction_group")

table_vendor <- 
  dbGetQuery(
    odbc_aws, 
    paste("
      SELECT id, name FROM vendor WHERE entity_id = ", t_id))

alpine_sd_2018_exp <- 
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT 
            posting_date, amount, description, type, 
            org1, org2, org3,
            cat1, cat2, cat3,
            fund1, fund2,
            vendor_id, account_number
          FROM transaction
          WHERE batch_id IN (
            SELECT id
            FROM batch
            WHERE entity_id = ", t_id, "
            AND status IN ('PROCESSED', 'PROCESSING', 'DONTDELETE'))
          AND fiscal_year = 2018
          AND type = 1")) %>% 
  left_join(table_transaction_group, by = c("org1" = "id")) %>% 
    select(-org1) %>% rename(org1 = name) %>% 
  left_join(table_transaction_group, by = c("org2" = "id")) %>% 
    select(-org2) %>% rename(org2 = name) %>% 
  left_join(table_transaction_group, by = c("org3" = "id")) %>% 
    select(-org3) %>% rename(org3 = name) %>% 
  left_join(table_transaction_group, by = c("cat1" = "id")) %>% 
    select(-cat1) %>% rename(cat1 = name) %>% 
  left_join(table_transaction_group, by = c("cat2" = "id")) %>% 
    select(-cat2) %>% rename(cat2 = name) %>% 
  left_join(table_transaction_group, by = c("cat3" = "id")) %>% 
    select(-cat3) %>% rename(cat3 = name) %>% 
  left_join(table_transaction_group, by = c("fund1" = "id")) %>% 
    select(-fund1) %>% rename(fund1 = name) %>% 
  left_join(table_transaction_group, by = c("fund2" = "id")) %>% 
    select(-fund2) %>% rename(fund2 = name) %>% 
  left_join(table_vendor, by = c("vendor_id" = "id")) %>% 
    select(-vendor_id) %>% rename(vendor_name = name) %>% 
  select(type, posting_date, amount, vendor_name, description,
         org1, org2, org3, cat1, cat2, cat3, fund1, fund2)

distinct_vendors <- 
  alpine_sd_2018_exp %>% 
  distinct(vendor_name)

alpine_sd_2018_exp %>% 
  select(-type) %>% 
  filter(
    str_detect(vendor_name, regex("^not", ignore_case = TRUE)) |
    str_detect(vendor_name, regex("U S Bank", ignore_case = TRUE))) %>% 
  write_csv(
    "~/3 Project Support/Transparency-Research/Alpine SD 2018 Expenses - Sample.csv",
    na = "")

alpine_sd_2018_exp %>% 
  select(-type) %>% 
  write_csv(
    "~/3 Project Support/Transparency-Research/Alpine SD 2018 Expenses.csv",
    na = "")
```

# DBMS Disconnection

```{r}
dbDisconnect()
```