---
title: "Utah Local Governments Trust & Alliant Insurance Services"
author: "Michael Jensen"
output: html_notebook
---
# Program Description

**Purpose**

A concerned citizen wants to know why the information Utah Local Governments Trust uploaded to Transparent Utah doesn't contain expenses paid to Alliant Insurance Services, Inc.

**Input(s)**

```{r}
dsn_aws <- "transpAWS"
```

**Comments**

2019-11-12 Update:

After I searched the Transparent Utah data for the supposedly missing information, I emailed ULGT to ask about the payment. Jody Pettet, Manager, responded to my email and stated that the payment would not appear in the Transparent Utah data because it was booked to the Balance Sheet under Prepaid Expenses. Each month, then, a journal entry was made to amortize a portion of that prepaid expense. The journal entries are reported to Transparent Utah, but have a vendor of "Not Applicable" because the transaction is a journal entry rather than a cash disbursement.

My conclusions, which I shared with Auditor Dougall, are:

* ULGT complied with Transparent Utah reporting requirements.
* The concerned citizen is understandably confused as to why the payment is not present in the Transparent Utah data.
* Transparent Utah is not designed to display the type of information that the concerned citizen wanted to see.

Discussing this problem with coworkers from the Financial Audit staff led to me discovering that, for entities operating on accrual-based accounting, revenues are not the same thing as cash receipts, and expenses are not the same thing as cash disbursements. 

# Libraries and Data Sources

```{r}
library(odbc)
library(tidyverse)

odbc_aws <- dbConnect(odbc::odbc(), dsn_aws)
rm(dsn_aws)
```

# Execution

The Transparent Utah ID for Utah Local Governments Trust is 935.

```{r}
trxns <- 
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT 
            posting_date, amount, fiscal_year, description, t.type, 
            tg1.name AS org1, tg2.name AS org2, tg3.name AS org3,
            tg4.name AS cat1, tg4.name AS cat2, tg6.name AS cat3,
            tg7.name AS fund1, tg8.name AS fund2,
            v.name AS vendor_name, account_number
          FROM transaction AS t
          LEFT JOIN transaction_group AS tg1
            ON t.org1 = tg1.id
          LEFT JOIN transaction_group AS tg2
            ON t.org2 = tg2.id
          LEFT JOIN transaction_group AS tg3
            ON t.org3 = tg3.id
          LEFT JOIN transaction_group AS tg4
            ON t.cat1 = tg4.id
          LEFT JOIN transaction_group AS tg5
            ON t.cat2 = tg5.id
          LEFT JOIN transaction_group AS tg6
            ON t.cat3 = tg6.id
          LEFT JOIN transaction_group AS tg7
            ON t.fund1 = tg7.id
          LEFT JOIN transaction_group AS tg8
            ON t.fund2 = tg8.id
          LEFT JOIN vendor AS v
            ON t.vendor_id = v.id
          WHERE batch_id IN (
            SELECT id
            FROM batch
            WHERE entity_id = ", 935, "
            AND status IN ('PROCESSED', 'PROCESSING', 'DONTDELETE'))"))

vendors <- 
  trxns %>% 
  distinct(vendor_name)
```

The concerned citizen is correct—the payments to Alliant Insurance Services are not present in Transparent Utah.

# DBMS Disconnection

```{r}
dbDisconnect(odbc_aws)
```