---
title: "AISU - Where Did the Money Go?"
author: "Michael Jensen"
date: "July 2019"
output:
  html_document:
    df_print: paged
    toc: yes
  html_notebook:
    toc: yes
---
***
# Background

The board of directors of the American International School of Utah (AISU), a charter school, voted that the school close no later than August 15, 2019 (["American International School of Utah directors vote to close school"](https://www.ksl.com/article/46548603/american-international-school-of-utah-directors-vote-to-close-school)). Auditor John Dougall was appointed interim director of the charter school (["State auditor named interim director of shuttered Utah charter school"](https://www.ksl.com/article/46595459/state-auditor-named-interim-director-of-shuttered-utah-charter-school)) and directed several members of his staff to investigate AISU's financial records.

```{r, echo=FALSE}
# Set up and query AISU's Transparency data:
library(knitr)
library(odbc)
library(scales)
library(tidyverse)

odbc_aws <- dbConnect(odbc::odbc(), "transpAWS")
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

table_tg <- dbGetQuery(odbc_aws, "SELECT id, name FROM transaction_group")
aisu_vendors  <- 
  dbGetQuery(odbc_aws, "SELECT id, name FROM vendor WHERE entity_id = 999")

aisu_t_data <- 
  list(
    summary_table =
      dbGetQuery(
        odbc_aws, 
        "SELECT trx_type, fiscal_year, total, tg.name
        FROM summary
        JOIN transaction_group AS tg
        ON summary.trx_group_id = tg.id
        WHERE entity_id = 999") %>% 
      arrange(desc(total)),
    
    trans_table_exp =
      dbGetQuery(
        odbc_aws,
        "SELECT 
          fiscal_year, posting_date, amount, description,
          org1, org2, cat1, cat2, cat3, fund1, vendor_id
        FROM transaction
        WHERE batch_id IN (
          SELECT id
          FROM batch
          WHERE entity_id = 999 
          AND status IN ('PROCESSED', 'DONTDELETE'))
        AND type = 1") %>% 
      left_join(table_tg, by = c("org1" = "id")) %>% 
        select(-org1) %>% rename(org1 = name) %>% 
      left_join(table_tg, by = c("org2" = "id")) %>% 
        select(-org2) %>% rename(org2 = name) %>% 
      left_join(table_tg, by = c("cat1" = "id")) %>% 
        select(-cat1) %>% rename(cat1 = name) %>% 
      left_join(table_tg, by = c("cat2" = "id")) %>% 
        select(-cat2) %>% rename(cat2 = name) %>% 
      left_join(table_tg, by = c("cat3" = "id")) %>% 
        select(-cat3) %>% rename(cat3 = name) %>% 
      left_join(table_tg, by = c("fund1" = "id")) %>% 
        select(-fund1) %>% rename(fund1 = name) %>% 
      left_join(aisu_vendors, by = c("vendor_id" = "id")) %>% 
        rename(vendor_name = name) %>% 
      arrange(desc(amount)), 
    
    trans_table_rev =
      dbGetQuery(
        odbc_aws,
        "SELECT 
          fiscal_year, posting_date, amount, description,
          org1, org2, cat1, cat2, cat3, fund1, vendor_id
        FROM transaction
        WHERE batch_id IN (
          SELECT id
          FROM batch
          WHERE entity_id = 999 
          AND status IN ('PROCESSED', 'DONTDELETE'))
        AND type = 2") %>% 
      left_join(table_tg, by = c("org1" = "id")) %>% 
        select(-org1) %>% rename(org1 = name) %>% 
      left_join(table_tg, by = c("org2" = "id")) %>% 
        select(-org2) %>% rename(org2 = name) %>% 
      left_join(table_tg, by = c("cat1" = "id")) %>% 
        select(-cat1) %>% rename(cat1 = name) %>% 
      left_join(table_tg, by = c("cat2" = "id")) %>% 
        select(-cat2) %>% rename(cat2 = name) %>% 
      left_join(table_tg, by = c("cat3" = "id")) %>% 
        select(-cat3) %>% rename(cat3 = name) %>% 
      left_join(table_tg, by = c("fund1" = "id")) %>% 
        select(-fund1) %>% rename(fund1 = name) %>% 
      left_join(aisu_vendors, by = c("vendor_id" = "id")) %>% 
        rename(vendor_name = name) %>% 
      arrange(desc(amount)), 
    
    vendors = 
      dbGetQuery(
        odbc_aws,
        "SELECT id, name
        FROM vendor
        WHERE entity_id = 999"),
    
    vendor_summary = 
      dbGetQuery(
        odbc_aws,
        "SELECT type, fiscal_year, total, v.name, vendor_id
        FROM vendor_summary AS vs
        JOIN vendor AS v
        ON vs.vendor_id = v.id
        WHERE vs.entity_id = 999") %>% 
      arrange(desc(total)))

rm(aisu_vendors)
```

```{r, eval=FALSE}
write_csv(aisu_t_data$summary_table,   "aisu_by_year_by_classification.csv")
write_csv(aisu_t_data$trans_table_exp, "aisu_expenses.csv")
write_csv(aisu_t_data$trans_table_rev, "aisu_revenues.csv")
write_csv(aisu_t_data$vendors,         "aisu_vendors.csv")
write_csv(aisu_t_data$vendor_summary,  "aisu_by_year_by_vendor.csv")
```

***
# Who are the top-paid vendors, 2015-2019?

```{r}
aisu_t_data$vendor_summary %>% 
  filter(type == 1) %>% 
  group_by(fiscal_year, name) %>% 
  summarize(amount = sum(total)) %>% 
  arrange(desc(amount)) %>% 
  mutate(amount = dollar(amount)) %>% 
  head(n = 15) %>% 
  kable()
```

## What are the expense transactions associated with the "Not Applicable" and "Not Provided" vendors?

```{r}
vendor_is_na <- 
  aisu_t_data[["vendors"]] %>% 
  mutate(name = str_to_lower(.[["name"]]))

vendor_is_np <- 
  aisu_t_data[["vendors"]] %>% 
  mutate(name = str_to_lower(.[["name"]]))

vendor_is_na <- 
  vendor_is_na[str_detect(vendor_is_na$name, "^not a"),]

vendor_is_np <- 
  vendor_is_np[str_detect(vendor_is_np$name, "^not p"),]
```

### FY 2018 "Not Applicable" vendors are tied to the following transactions:

```{r}
aisu_t_data$trans_table_exp %>% 
  filter(fiscal_year == 2018, vendor_id %in% vendor_is_na$id) %>% 
  select(posting_date, amount, description, cat1, cat2, cat3) %>% 
  arrange(desc(amount)) %>% 
  mutate(amount = dollar(amount)) %>% 
  head(n = 15) %>% 
  kable()
```

### FY 2017 "Not Provided" vendors are tied to the following transactions:

```{r}
aisu_t_data$trans_table_exp %>% 
  filter(fiscal_year == 2017, vendor_id %in% vendor_is_np$id) %>% 
  select(posting_date, amount, description, cat1, cat2, cat3) %>% 
  arrange(desc(amount)) %>% 
  mutate(amount = dollar(amount)) %>% 
  head(n = 15) %>% 
  kable()
```

### FY 2016 "Not Provided" vendors are tied to the following transactions:

```{r}
aisu_t_data$trans_table_exp %>% 
  filter(fiscal_year == 2016, vendor_id %in% vendor_is_np$id) %>% 
  select(posting_date, amount, description, cat1, cat2, cat3) %>% 
  arrange(desc(amount)) %>% 
  mutate(amount = dollar(amount)) %>% 
  head(n = 15) %>% 
  kable()
```

### FY 2018 "Not Provided" vendors are tied to the following transactions:

```{r}
aisu_t_data$trans_table_exp %>% 
  filter(fiscal_year == 2018, vendor_id %in% vendor_is_np$id) %>% 
  select(posting_date, amount, description, cat1, cat2, cat3) %>% 
  arrange(desc(amount)) %>% 
  mutate(amount = dollar(amount)) %>% 
  head(n = 15) %>% 
  kable()
```

### FY 2015 "Not Provided" vendors are tied to the following transactions:

```{r}
aisu_t_data$trans_table_exp %>% 
  filter(fiscal_year == 2015, vendor_id %in% vendor_is_np$id) %>% 
  select(posting_date, amount, description, cat1, cat2, cat3) %>% 
  arrange(desc(amount)) %>% 
  mutate(amount = dollar(amount)) %>% 
  head(n = 15) %>% 
  kable()
```

## What are the transactions associated with Schoolhouse Galleria?

```{r}
vendor_is_sg <- 
  aisu_t_data[["vendors"]] %>% 
  mutate(name = str_to_lower(.[["name"]]))

vendor_is_sg <- 
  vendor_is_sg[str_detect(vendor_is_sg$name, "^schoolhouse"),]
```

2016:

```{r}
aisu_t_data$trans_table_exp %>% 
  filter(fiscal_year == 2016, vendor_id %in% vendor_is_sg$id) %>% 
  select(posting_date, amount, description, cat1, cat2, cat3) %>% 
  arrange(desc(amount)) %>% 
  mutate(amount = dollar(amount)) %>% 
  head(n = 15) %>% 
  kable()
```

2017:

```{r}
aisu_t_data$trans_table_exp %>% 
  filter(fiscal_year == 2017, vendor_id %in% vendor_is_sg$id) %>% 
  select(posting_date, amount, description, cat1, cat2, cat3) %>% 
  arrange(desc(amount)) %>% 
  mutate(amount = dollar(amount)) %>% 
  head(n = 15) %>% 
  kable()
```

2015:

```{r}
aisu_t_data$trans_table_exp %>% 
  filter(fiscal_year == 2015, vendor_id %in% vendor_is_sg$id) %>% 
  select(posting_date, amount, description, cat1, cat2, cat3) %>% 
  arrange(desc(amount)) %>% 
  mutate(amount = dollar(amount)) %>% 
  head(n = 15) %>% 
  kable()
```

2019:

```{r}
aisu_t_data$trans_table_exp %>% 
  filter(fiscal_year == 2019, vendor_id %in% vendor_is_sg$id) %>% 
  select(posting_date, amount, description, cat1, cat2, cat3) %>% 
  arrange(desc(amount)) %>% 
  mutate(amount = dollar(amount)) %>% 
  head(n = 15) %>% 
  kable()
```

2018:

```{r, warning=FALSE, message=FALSE}
aisu_t_data$trans_table_exp %>% 
  filter(fiscal_year == 2018, vendor_id %in% vendor_is_sg$id) %>% 
  select(posting_date, amount, description, cat1, cat2, cat3) %>% 
  arrange(desc(amount)) %>% 
  mutate(amount = dollar(amount)) %>% 
  head(n = 15) %>% 
  kable()
```

All expenses to Schoolhouse Galleria:

```{r}
sg_payments <- 
  aisu_t_data[["trans_table_exp"]] %>% 
  filter(vendor_id %in% vendor_is_sg$id)

sg_payments %>% 
  arrange(fiscal_year) %>% 
  kable()
```

Yearly total expenditures from AISU to Schoolhouse Galleria:

```{r}
sg_payments %>% 
  group_by(fiscal_year) %>% 
  summarize(total_exp = sum(amount)) %>% 
  mutate(total_exp = dollar(total_exp)) %>% 
  kable()
```

***
# "Schoolhouse" Vendors

## Schoolhouse Galleria, Inc. is another name for Schoolhouse Development, Inc. Are there any other "Schoolhouse" vendors for charter schools?

```{r}
vendor_contains_schoolhouse <- 
  dbGetQuery(
    odbc_aws,
    "SELECT DISTINCT v.id, v.name AS vendor_name, entity_id, e.name AS lea_name
    FROM vendor AS v
    LEFT JOIN entity AS e
    ON v.entity_id = e.id
    WHERE (
      LOWER(v.name) LIKE '%schoolhouse%'  OR
      LOWER(v.name) LIKE '%school house%' OR
      LOWER(v.name) LIKE '%galleria%'     OR
      LOWER(v.name) LIKE '%galeria%')
    AND (
      LOWER(v.name) NOT LIKE 'galeria, brooke'  AND
      LOWER(v.name) NOT LIKE 'galleria floral%' AND
      LOWER(v.name) NOT LIKE 'cafe galleria%')
    AND v.entity_id IN (
      SELECT id
      FROM entity
      WHERE govt_lvl = 'K12 Education')")

charter_vendor_contains_schoolhouse <-
  vendor_contains_schoolhouse[!str_detect(vendor_contains_schoolhouse$lea_name, "School District"),]

charter_vendor_contains_schoolhouse %>% 
  distinct(vendor_name, lea_name) %>% 
  select(lea_name, vendor_name) %>% 
  arrange(lea_name) %>% 
  kable()
```

```{r}
query_vendor_summary <- function(vendor_id) {
  # Query the vendor summary information for a given vendor, using the vendor ID.
  #
  # Arguments:
  #   vendor_id: The vendor's Transparency ID.
  #
  # Value:
  #   Data frame.
  
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT 
            e.name AS lea_name, 
            v.name AS vendor_name,
            vs.type AS trxn_type, vs.fiscal_year, vs.total AS amount
          FROM vendor_summary AS vs
          LEFT JOIN entity AS e
          ON vs.entity_id = e.id
          LEFT JOIN vendor AS v
          ON vs.vendor_id = v.id
          WHERE vs.vendor_id = ", vendor_id))
} 

sg_vendor_summary <- 
  map(charter_vendor_contains_schoolhouse$id, query_vendor_summary) %>% 
  bind_rows()

sg_vendor_summary %>%
  arrange(lea_name, fiscal_year) %>% 
  mutate(amount = dollar(amount)) %>% 
  kable()
```

## What about mention of a "Schoolhouse" vendor in the transaction descriptions for charter schools?

```{r}
trans_exp_contains_schoolhouse <- 
  dbGetQuery(
    odbc_aws,
    "SELECT DISTINCT description
    FROM transaction
    WHERE (
      LOWER(description) LIKE '%schoolhouse%' OR
      LOWER(description) LIKE '%school house%')
    AND batch_id IN (
      SELECT id
      FROM batch
      WHERE entity_id IN (
        SELECT id
        FROM entity
        WHERE govt_lvl = 'K12 Education')
      AND status IN ('PROCESSED', 'DONTDELETE'))")

trans_exp_contains_schoolhouse %>% kable()
```
