---
title: "AWS Boilerplate Code"
author: "Michael Jensen"
output: html_notebook
---
# Libraries and Data Sources

```{r, message=FALSE}
library(lubridate)
library(magrittr)
library(odbc)
library(scales)
library(tidyverse)

odbc_aws <- dbConnect(odbc::odbc(), "transpAWS")
```

# Code Templates - Transparent Utah Metadata

## Information Schema

```{sql, connection = odbc_aws, output.var = "info_schema_tables"}
SELECT *
FROM information_schema.tables
```

```{sql, connection=odbc_aws, output.var=transparency_table_names}
SELECT TABLE_NAME
FROM information_schema.tables
WHERE TABLE_SCHEMA = "transparency"
```

## Data Size

```{sql, connection = odbc_aws, output.var = "info_schema_size"}
SELECT table_schema AS 'Database', 
       table_name AS 'Table',
       ROUND(((DATA_LENGTH + INDEX_LENGTH) / 1024 / 1024), 2) AS 'Size in MB'
FROM information_schema.tables
ORDER BY (DATA_LENGTH + INDEX_LENGTH) DESC
```

```{r}
data_size_in_Mb <- 
  info_schema_size %>% 
  summarize(sum(`Size in MB`) %>% round()) %>% 
  as.numeric()

data_size_in_Gb <- 
  data_size_in_Mb %>% 
  divide_by(1000) %>% 
  round()
```

## Indexes

Create an index (permission to do so is currently denied):

```{sql, connection = odbc_aws}
CREATE INDEX transaction_batchid
ON transaction (batch_id)
```

View indexed variables:

```{sql, connection = odbc_aws, output.var = "indexed_variables"}
SELECT DISTINCT table_name, index_name
FROM information_schema.statistics
WHERE table_schema = 'transparency'
```

```{sql, connection = odbc_aws, output.var = "index_batch"}
SHOW INDEX FROM batch
```

```{sql, connection = odbc_aws, output.var = "index_entity"}
SHOW INDEX FROM entity
```

```{sql, connection = odbc_aws, output.var = "index_transaction"}
SHOW INDEX FROM transaction
```

## R Object Size

```{r}
entity_transactions %>% 
  object.size() %>% 
  print(units = "auto")
```

# Code Templates - Transparent Utah Data

## Entity Table

```{r}
table_entity <- 
  dbGetQuery(odbc_aws, "SELECT id, name FROM entity")

table_entity <- 
  dbGetQuery(odbc_aws, paste("
    SELECT id, name, govt_lvl, fiscal_period, payroll_period
    FROM entity
    WHERE id = ", t_id))
```

```{sql, connection=odbc_aws, output.var="entity_table"}
SELECT 
  name,
  govt_lvl,
  fiscal_period,
  payroll_period
FROM entity
WHERE id = ?t_id
```

```{sql, connection = odbc_aws, output.var = "count_entity"}
SELECT COUNT(*)
FROM entity
```

## Batch Table

```{r}
table_batch <- 
  dbGetQuery(
    odbc_aws,
    paste("
      SELECT
        id, upload_date, processed_date, file_record_count, file_total_amount,
        begin_txn_date, end_txn_date, status, status_message
      FROM batch
      WHERE entity_id = ", t_id, "
      ORDER BY upload_date DESC"))
```

```{sql, connection=odbc_aws, output.var="table_batch"}
SELECT 
  id,
  upload_date,
  processed_date,
  file_record_count,
  file_total_amount,
  begin_txn_date,
  end_txn_date,
  status,
  status_message
FROM batch
WHERE entity_id = ?t_id
AND status IN ('PROCESSED', 'PROCESSING', 'DONTDELETE')
ORDER BY upload_date DESC
```

```{sql, connection=odbc_aws, output.var="batch_table_status_options"}
SELECT DISTINCT status
FROM batch
```

```{sql, connection = odbc_aws, output.var = "count_batch"}
SELECT COUNT(*) FROM batch
```

```{sql, connection = odbc_aws, output.var = "count_deleted_batches"}
SELECT COUNT(*) FROM batch WHERE status = 'DELETED'
```

## Transaction Tables

**Remember**

* Transactions for the current and previous four fiscal years are stored in the 
transaction table. The remaining years are stored in separate tables (e.g., 
transaction_2009).

```{r}
trxns <- 
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT 
            posting_date, amount, fiscal_year, description, t.type, 
            tg1.name AS org1, tg2.name AS org2, tg3.name AS org3,
            tg4.name AS cat1, tg4.name AS cat2, tg6.name AS cat3,
            tg7.name AS fund1, tg8.name AS fund2,
            v.name AS vendor_name, account_number
          FROM transaction AS t
          LEFT JOIN transaction_group AS tg1
            ON t.org1 = tg1.id
          LEFT JOIN transaction_group AS tg2
            ON t.org2 = tg2.id
          LEFT JOIN transaction_group AS tg3
            ON t.org3 = tg3.id
          LEFT JOIN transaction_group AS tg4
            ON t.cat1 = tg4.id
          LEFT JOIN transaction_group AS tg5
            ON t.cat2 = tg5.id
          LEFT JOIN transaction_group AS tg6
            ON t.cat3 = tg6.id
          LEFT JOIN transaction_group AS tg7
            ON t.fund1 = tg7.id
          LEFT JOIN transaction_group AS tg8
            ON t.fund2 = tg8.id
          LEFT JOIN vendor AS v
            ON t.vendor_id = v.id
          WHERE batch_id IN (
            SELECT id
            FROM batch
            WHERE entity_id = ", t_id, "
            AND status IN ('PROCESSED', 'PROCESSING', 'DONTDELETE'))"))
```

```{r}
distinct_transactions <- 
  list(
    org1 = 
      transactions %>% 
      distinct(org1) %>% 
      arrange(org1),

    org2 = 
      transactions %>% 
      distinct(org2) %>% 
      arrange(org2),
    
    org3 = 
      transactions %>% 
      distinct(org3) %>% 
      arrange(org3),
    
    cat1 = 
      transactions %>% 
      distinct(cat1) %>% 
      arrange(cat1),
    
    cat2 = 
      transactions %>% 
      distinct(cat2) %>% 
      arrange(cat2),
    
    cat3 = 
      transactions %>% 
      distinct(cat3) %>% 
      arrange(cat3),
    
    fund1 =
      transactions %>% 
      distinct(fund1) %>% 
      arrange(fund1),
    
    fund2 = 
      transactions %>% 
      distinct(fund2) %>% 
      arrange(fund2),
    
    ucoa =
      transactions %>% 
      distinct(account_number) %>% 
      arrange(account_number))
```

```{sql, connection = odbc_aws, output.var = "count_transactions"}
SELECT COUNT(*) FROM transaction
```

```{sql, connection = odbc_aws, output.var = "count_deleted_transactions"}
SELECT COUNT(*) 
FROM transaction 
WHERE batch_id IN (
  SELECT id
  FROM batch
  WHERE status = 'DELETED')
```

## Transaction Group Table

```{r}
table_transaction_group <-  
  dbGetQuery(odbc_aws, "SELECT id, name FROM transaction_group")
```

```{sql, connection=odbc_aws, output.var="table_transaction_group"}
SELECT id, name
FROM transaction_group
```

## Summary Table

**Remember**

The information in the Summary Table is for summarizing transactions by `org`, `cat`, `fund`, `program`, and `function`. It is not for summarizing data by fiscal year (do that using the Transaction Table).

```{sql, connection=odbc_aws, output.var="table_summary"}
SELECT *
FROM summary
WHERE entity_id = ?t_id
```

## Vendor Table

**Remember**

The Vendor Table contains all vendors uploaded to Transparency, which means that
it contains vendors that have been deleted. The Vendor Summary Table contains 
current information.

```{r}
table_vendor <- 
  dbGetQuery(odbc_aws, "SELECT id, name, entity_id FROM vendor")
```

```{sql, connection=odbc_aws, output.var="table_vendor"}
SELECT *
FROM vendor
WHERE entity_id = ?t_id
```

## Vendor Summary Table

```{r}
table_vendor_summary <- 
  dbGetQuery(
    odbc_aws, 
    "SELECT entity_id, type, fiscal_year, total, vendor_id FROM vendor_summary")
```

```{r}
vendor_summary <- 
  dbGetQuery(
    odbc_aws,
    "SELECT type, fiscal_year, total, name AS vendor_name
    FROM vendor_summary
    LEFT JOIN vendor
      ON vendor_summary.vendor_id = vendor.id
    WHERE vendor_summary.entity_id = 259")
```

```{sql, connection=odbc_aws, output.var="table_vendor_summary"}
SELECT *
FROM vendor_summary
WHERE entity_id = ?t_id
```

# Close

```{r}
dbDisconnect(odbc_aws)
```

# Workspace

```{r}
t_id <- 207
```

```{r}

```
