---
title: "U.S. Census Bureau Request for 2016 & 2017 Transparency Data"
author: "Michael Jensen"
date: "February 2019"
output: html_notebook
---
# Program Description

**Purpose**

Provide 2016 and 2017 Transparency data for counties, cities, towns, and  interlocal, local, and special service districts to the U.S. Census Bureau's  Local Finance Statistics Branch.

**Inputs**

* The name of the ODBC connection to AWS.

**Outputs**

* One .csv file of 2016 and 2017 Transparency data for each of the following local government groups:
    + Counties
    + Cities and towns
    + Interlocals
    + Local districts
    + Special service districts

# Libraries and Data Source(s)

```{r}
library(odbc)
library(tidyverse)

odbc_aws <- dbConnect(odbc::odbc(), "transpAWS")
```

# Function Definitions

## query_entity_transactions_2016_2017()

```{r}
query_entity_transactions_2016_2017 <- function(govt_type) {
  # Query entity names, IDs, and 2016 and 2017 transactions for entities of the
  # specified government type.
  #
  # Args:
  #   govt_type (chr): The government type to query, capitalized and surrounded
  #     by single quotes (i.e., 'COUNTY', 'CITY', 'INTERLOCAL', 'LOCAL 
  #     DISTRICTS', or 'SERVICE DISTRICTS').
  #
  # Returns:
  #   A data frame containing 2016 and 2017 data from the Transaction Table,
  #   joined with the corresponding entity name and ID, for entities of the
  #   specified government type.
  
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT 
            posting_date,
            amount,
            batch_id,
            fiscal_year,
            description,
            type AS transaction_type,
            org1, org2, org3, org4,
            cat1, cat2, cat3, cat4,
            fund1, fund2,
            vendor_id,
            account_number
          FROM transaction
          WHERE batch_id IN (
            SELECT id
            FROM batch
            WHERE entity_id IN (
              SELECT id
              FROM entity
              WHERE govt_lvl = ", govt_type, "))
          AND fiscal_year IN (2016, 2017)
          AND type IN (1, 2, 3)")) %>% 
    left_join(
      dbGetQuery(
        odbc_aws,
        paste("
              SELECT 
                batch.id        AS batch_id,
                batch.entity_id AS entity_id,
                entity.name     AS entity_name
              FROM batch
              JOIN entity
              ON batch.entity_id = entity.id
              WHERE batch.entity_id IN (
                SELECT id
                FROM entity
                WHERE govt_lvl IN (", govt_type, "))")),
      by = "batch_id") %>% 
    select(entity_name, entity_id, fiscal_year, transaction_type, 
           posting_date, amount, description, vendor_id, 
           org1, org2, org3, org4, cat1, cat2, cat3, cat4, fund1, fund2,
           account_number)
}
```

# Execution

## SQL queries

```{sql, connection=odbc_aws}
SELECT DISTINCT level_key
FROM government_level
```

```{sql, connection=odbc_aws, output.var=entity_information}
SELECT
  id            AS entity_id,
  name          AS entity_name,
  govt_lvl,
  fiscal_period AS fy_begin_month
FROM entity
WHERE govt_lvl IN (
  'CITY',
  'COUNTY',
  'INTERLOCAL',
  'LOCAL DISTRICTS',
  'SERVICE DISTRICTS')
```

```{sql, connection=odbc_aws, output.var=transaction_group_table}
SELECT id, name
FROM transaction_group
```

```{sql, connection=odbc_aws, output.var=vendor_table}
SELECT
  id   AS vendor_id,
  name AS vendor_name,
  entity_id
FROM vendor
WHERE entity_id IN (
  SELECT id
  FROM entity
  WHERE govt_lvl IN (
    'CITY',
    'COUNTY',
    'INTERLOCAL',
    'LOCAL DISTRICTS',
    'SERVICE DISTRICTS'))
```

## Create reports

```{r}
government_types <- 
  c("'COUNTY'", "'CITY'", "'INTERLOCAL'", "'LOCAL DISTRICTS'", 
    "'SERVICE DISTRICTS'")

transaction_data_2016_2017 <- 
  map(government_types, 
      query_entity_transactions_2016_2017) 
  
names(transaction_data_2016_2017) <- 
  government_types
```

## Check report quality

```{r}
summary(entity_information)
entity_information %>% distinct(govt_lvl)
entity_information %>% distinct(fy_begin_month)

summary(transaction_group_table)
summary(vendor_table)
summary(transaction_data_2016_2017[["'COUNTY'"]])
summary(transaction_data_2016_2017[["'CITY'"]])
summary(transaction_data_2016_2017[["'INTERLOCAL'"]])
summary(transaction_data_2016_2017[["'LOCAL DISTRICTS'"]])
summary(transaction_data_2016_2017[["'SERVICE DISTRICTS'"]])
```

## Export

```{r}
write_csv(entity_information, 
          "utah_entity_information.csv")

write_csv(transaction_group_table, 
          "utah_id_crosswalk_transactions.csv")

write_csv(vendor_table, 
          "utah_id_crosswalk_vendors.csv")

write_csv(transaction_data_2016_2017[["'COUNTY'"]], 
          "utah_2016_2017_county.csv")

transaction_data_2016_2017[["'CITY'"]] %>% 
  filter(fiscal_year == 2016) %>% 
  write_csv("utah_2016_city.csv")

transaction_data_2016_2017[["'CITY'"]] %>% 
  filter(fiscal_year == 2017) %>% 
  write_csv("utah_2017_city.csv")

write_csv(transaction_data_2016_2017[["'INTERLOCAL'"]], 
          "utah_2016_2017_interlocal.csv")

write_csv(transaction_data_2016_2017[["'LOCAL DISTRICTS'"]], 
          "utah_2016_2017_local.csv")

write_csv(transaction_data_2016_2017[["'SERVICE DISTRICTS'"]], 
          "utah_2016_2017_service.csv")
```

# DBMS Disconnection

```{r}
dbDisconnect(odbc_aws)
```