---
title: "Reporting Depth"
author: "Michael Jensen"
date: "September 2018"
output: html_notebook
---
# Program Description

Determine whether there are Organization, Category, Fund, Program, or Function levels that governments do not use when reporting to Transparency.

**Notes**

The following tables have been replaced by the Transaction_group Table and are no longer used:

* cat_summary
* category
* fund
* fund_summary
* org_summary
* organization

# Program

## Packages & Data Connections

```{r, message = FALSE}
library(magrittr)
library(odbc)
library(tidyverse)

odbc_aws <- dbConnect(odbc::odbc(), "transpAWS")
```

# Org, Cat, Fund, Program, & Function Reporting Depth
## How deep do governments report organization level information?

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id IN (
  SELECT entity_id
  FROM batch
  WHERE id IN (
    SELECT batch_id
    FROM transaction
    WHERE org10 IS NOT NULL))
```

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id IN (
  SELECT entity_id
  FROM batch
  WHERE id IN (
    SELECT batch_id
    FROM transaction
    WHERE org9 IS NOT NULL))
```

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id IN (
  SELECT entity_id
  FROM batch
  WHERE id IN (
    SELECT batch_id
    FROM transaction
    WHERE org8 IS NOT NULL))
```

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id IN (
  SELECT entity_id
  FROM batch
  WHERE id IN (
    SELECT batch_id
    FROM transaction
    WHERE org7 IS NOT NULL))
```

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id IN (
  SELECT entity_id
  FROM batch
  WHERE id IN (
    SELECT batch_id
    FROM transaction
    WHERE org6 IS NOT NULL))
```

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id IN (
  SELECT entity_id
  FROM batch
  WHERE id IN (
    SELECT batch_id
    FROM transaction
    WHERE org5 IS NOT NULL))
```

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id IN (
  SELECT entity_id
  FROM batch
  WHERE id IN (
    SELECT batch_id
    FROM transaction
    WHERE org4 IS NOT NULL))
```

## How deep to governments report category level information?

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id IN (
  SELECT entity_id
  FROM batch
  WHERE id IN (
    SELECT batch_id
    FROM transaction
    WHERE cat7 IS NOT NULL))
```

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id IN (
  SELECT entity_id
  FROM batch
  WHERE id IN (
    SELECT batch_id
    FROM transaction
    WHERE cat6 IS NOT NULL))
```

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id IN (
  SELECT entity_id
  FROM batch
  WHERE id IN (
    SELECT batch_id
    FROM transaction
    WHERE cat5 IS NOT NULL))
```

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id IN (
  SELECT entity_id
  FROM batch
  WHERE id IN (
    SELECT batch_id
    FROM transaction
    WHERE cat4 IS NOT NULL))
```

## How deep do governments report fund level information

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id IN (
  SELECT entity_id
  FROM batch
  WHERE id IN (
    SELECT batch_id
    FROM transaction
    WHERE fund4 IS NOT NULL))
```

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id IN (
  SELECT entity_id
  FROM batch
  WHERE id IN (
    SELECT batch_id
    FROM transaction
    WHERE fund3 IS NOT NULL))
```

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id IN (
  SELECT entity_id
  FROM batch
  WHERE id IN (
    SELECT batch_id
    FROM transaction
    WHERE fund2 IS NOT NULL))
```

## How deep do governments report program level information?

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id IN (
  SELECT entity_id
  FROM batch
  WHERE id IN (
    SELECT batch_id
    FROM transaction
    WHERE program7 IS NOT NULL))
```

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id IN (
  SELECT entity_id
  FROM batch
  WHERE id IN (
    SELECT batch_id
    FROM transaction
    WHERE program6 IS NOT NULL))
```

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id IN (
  SELECT entity_id
  FROM batch
  WHERE id IN (
    SELECT batch_id
    FROM transaction
    WHERE program5 IS NOT NULL))
```

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id IN (
  SELECT entity_id
  FROM batch
  WHERE id IN (
    SELECT batch_id
    FROM transaction
    WHERE program4 IS NOT NULL))
```

## How deep to governments report function level information?

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id IN (
  SELECT entity_id
  FROM batch
  WHERE id IN (
    SELECT batch_id
    FROM transaction
    WHERE function7 IS NOT NULL))
```

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id IN (
  SELECT entity_id
  FROM batch
  WHERE id IN (
    SELECT batch_id
    FROM transaction
    WHERE function6 IS NOT NULL))
```

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id IN (
  SELECT entity_id
  FROM batch
  WHERE id IN (
    SELECT batch_id
    FROM transaction
    WHERE function5 IS NOT NULL))
```

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id IN (
  SELECT entity_id
  FROM batch
  WHERE id IN (
    SELECT batch_id
    FROM transaction
    WHERE function4 IS NOT NULL))
```

# Identify meaningful levels of data:

Several governments report non-meaninful levels of data (e.g., the description is "0"). The following pieces of code help determine how deep governments are reporting meaningful data.

```{r}
t_transaction_group_table$id <- as.integer(t_transaction_group_table$id)

level_list  <- list(org_level = list(), cat_level = list(), fund_level = list(),
                    program_level = list(), function_level = list())
```

```{r}
level_names <- c("org", "cat", "fund", "program", "function")

for (level in level_names) {
  level_name  <- level 

  if (level_name == "org") {
    level_depth <- 10
  } else if (level_name == "cat" || 
             level_name == "program" || 
             level_name == "function") {
    level_depth <- 7
  } else if (level_name == "fund") {
    level_depth <- 4
  } 

  for (i in 1:level_depth) {
    entity_transactions_all[ , paste0(level_name, i)] <- 
      as.integer(entity_transactions_all[ , paste0(level_name, i)])
    
    level_list[[paste0(level_name, "_level")]][[i]] <- 
      entity_transactions_all %>% 
      select(paste0(level_name, i)) %>% 
      unique
    
    colnames(level_list[[paste0(level_name, "_level")]][[i]])[[1]] <- 
      "id"
    
    level_list[[paste0(level_name, "_level")]][[i]] <- 
      merge(level_list[[paste0(level_name, "_level")]][[i]],
            t_transaction_group_table,
            by.x = "id", by.y = "id") %>% 
      filter(name != "0")
  }
  rm(i)
}
rm(level, level_name, level_depth, level_names)
```

# Workspace

## Inputs
### Define the Transparency ID and verify it is for the correct government:

```{r}
transparency_id <- 25
```

```{sql, connection = odbc_aws}
SELECT name
FROM entity
WHERE id = ?transparency_id
```

### Define the Batch ID:

```{r}
# batch_id <- 
```

# Close

```{r}
dbDisconnect(odbc_aws)
rm(list = ls())
```