---
title: "Transparency Queue"
author: "Michael Jensen"
output: html_notebook
---
# Program Description

Determine the number of files waiting to be processed, and estimate how long it will take for the files in the queue to be processed.

# Program

```{r}
library(odbc)
library(lubridate)
library(tidyverse)

odbc_aws <- dbConnect(odbc::odbc(), "transpAWS")
```

Assuming that a processed_date value that is 21 days or later than the upload_date value indicates a subsequent processing of the batch and therefore should be filtered from the data set, what was the upload-to-process time for the batch with the highest record count?

```{sql, connection=odbc_aws, output.var="processed_batches"}
SELECT 
  upload_date,
  processed_date,
  file_record_count
FROM batch
WHERE status = "PROCESSED"
```

```{r}
processed_batches <- 
  processed_batches %>% 
  mutate(time_difference = difftime(processed_date,
                                    upload_date,
                                    units = "days"))

highest_records_process_time <- 
  processed_batches %>% 
  filter(processed_date <= (upload_date + days(21))) %>% 
  filter(file_record_count == max(file_record_count))

processed_batches_filtered <- 
  processed_batches %>% 
  filter(time_difference <= highest_records_process_time$time_difference &
           file_record_count > 0)

rm(highest_records_process_time)

processed_batches_filtered$file_record_count <- 
  processed_batches_filtered$file_record_count %>% 
  as.numeric()

processed_batches_filtered <- 
  processed_batches_filtered %>% 
  mutate(days_per_record = time_difference / file_record_count)

days_per_record_mean <- 
  mean(processed_batches_filtered$days_per_record) %>% 
  as.numeric()

days_per_record_median <- 
  median(processed_batches_filtered$days_per_record) %>% 
  as.numeric()
```

```{sql, connection=odbc_aws, output.var="batches_in_queue"}
SELECT 
  entity.name,
  batch.upload_date,
  batch.user_record_count
FROM batch
JOIN entity
ON entity.id = batch.entity_id
WHERE status = "UPLOADED"
```

```{r}
total_uploaded_records <- 
  sum(batches_in_queue$user_record_count) %>% 
  as.numeric()

mean_estimated_days_to_process <- 
  days_per_record_mean * total_uploaded_records

median_estimated_days_to_process <- 
  days_per_record_median * total_uploaded_records
```


Well... that didn't work out like I thought it would. The estimated days are way too high...

```{r}
longest_time_in_queue <- 
  difftime(now(), min(batches_in_queue$upload_date), units = "days") %>% 
  round(digits = 1) %>% 
  print()
```
