---
title: "U.S. Census Bureau Request for Transparent Utah Data"
author: "Michael Jensen"
output: html_notebook
---
# Program Description

**Purpose**

Respond to a request from the Local Finance Statistics Branch of the U.S. Census Bureau for expense and revenue transactions from Transparent Utah for the following local governments: counties, cities and towns, and interlocal, local, and special service districts.

**Inputs**

* The name of the ODBC connection to AWS.
* The name of the ODBC connection to Salesforce.
* The two fiscal years to query, as requested by the Census Bureau.

```{r}
dsn_aws <- "transpAWS"
dsn_sf  <- "Salesforce"

fy_1 <- 2017
fy_2 <- 2018
```

**Outputs**

* One .csv file per government type containing the following fields from the Transparent Utah Transaction Table, for expense and revenue transactions from active governments:
  * entity_name
  * entity_id (i.e., Transparency ID)
  * fiscal_year
  * transaction_type
  * amount
  * description
  * org1, org2, org3, org4
  * cat1, cat2, cat3, cat4
  * fund1, fund2
  * account_number
* A .csv file of the Entity Table, containing the following fields for entities that have a `govt_lvl` value of `COUNTY`, `CITY`, `INTERLOCAL`, `LOCAL DISTRICTS`, or `SERVICE DISTRICTS`:
  * entity_id  (i.e., Transparency ID)
  * entity_name
  * govt_lvl
  * fiscal_period (i.e., the first month of the fiscal year)
* A .csv file of the Transaction Group Table, containing the following fields:
  * id
  * name

**Comments**

2019-11-11 Update:

* I considered joining the data from the Transaction Table with the data from the Transaction Group table. Doing so would have allowed me to send the Census Bureau a .csv file that wouldn't require additional joining in order to understand the information. I decided not to do so for the following reasons:

  * The email request I received asked for the same information I sent last year, so changing the format of the data I send the Census Bureau may mean extra work for whoever receives and processes the data.
  * Merging the data is a simple process. The analysts at the Census Bureau are more than capable of merging the data if they need to do so.

# Libraries and Data Source(s)

```{r, message=FALSE}
library(odbc)
library(tidyverse)

odbc_aws <- dbConnect(odbc::odbc(), dsn_aws)
odbc_sf  <- dbConnect(odbc::odbc(), dsn_sf)
rm(dsn_aws, dsn_sf)
```

# Function Definitions

## Argument Definitions

```{r}
  #   active_govts (tibble): The tibble containing the Transparency ID, entity
  #     name, government level (government type), and beginning month of the 
  #     entity's fiscal year for every active goverment that is a county, city 
  #     or town, or interlocal, local, or special service district.
  #   csv_name (char): The name of the .csv file.
  #   entity_name (char): The name of the government.
  #   fy_1 (num): The first fiscal year to query, as requested by the U.S.
  #     Census Bureau.
  #   fy_2 (num): The second fiscal year to query, as requested by the U.S.
  #     Census Bureau.
  #   govt_lvl (char): The government level to query, capitalized (COUNTY, CITY,
  #     INTERLOCAL, LOCAL DISTRICT, SERVICE DISTRICT).
  #   field_name (char): The field to query (e.g., "govt_lvl").
  #   report_name (tibble): The name of the tibble to export.
  #   t_id (num): The entity's Transparency ID, as queried from Salesforce
  #     rather than Transparency.
```

## `create_govt_lvl_report`

```{r}
create_govt_lvl_report <- function(active_govts, govt_lvl, fy_1, fy_2) {
  # Create the government level report requested by the U.S. Census Bureau.
  #
  # Arguments:
  #   active_govts (tibble): The tibble containing the Transparency ID, entity
  #     name, government level (government type), and beginning month of the 
  #     entity's fiscal year for every active goverment that is a county, city 
  #     or town, or interlocal, local, or special service district.
  #   govt_lvl (char): The government level to query, capitalized (COUNTY, CITY,
  #     INTERLOCAL, LOCAL DISTRICT, SERVICE DISTRICT).
  #   fy_1 (num): The first fiscal year to query, as requested by the U.S.
  #     Census Bureau.
  #   fy_2 (num): The second fiscal year to query, as requested by the U.S.
  #     Census Bureau.
  #
  # Value:
  #   Tibble.
  
  active_govts %>% 
    filter(govt_lvl == !!govt_lvl) %>% 
    .[["t_id"]] %>% 
    map(query_trxn_table, fy_1, fy_2) %>% 
    bind_rows() %>% 
    left_join(active_govts, by = "t_id") %>% 
    select(
      entity_name, entity_id = t_id, fiscal_year, transaction_type,
      amount, description, org1, org2, org3, org3, cat1, cat2,
      cat3, cat4, fund1, fund2, account_number)
}
```

## `query_entity_table`

```{r}
query_entity_table <- function(t_id, field_name) {
  # Query information from the AWS Entity Table.
  #
  # Arguments:
  #   t_id (num): The entity's Transparency ID, as queried from Salesforce
  #     rather than Transparency.
  #   field_name (char): The field to query (e.g., "govt_lvl").
  #
  # Value:
  #   A vector with length = 1 (scalar).

  dbGetQuery(
    odbc_aws,
    paste("
      SELECT ", field_name, " AS field
      FROM entity
      WHERE id = ", t_id)) %>% 
    .[["field"]]
}
```

## `query_trxn_table`

```{r}
query_trxn_table <- function(t_id, fy_1, fy_2) {
  # Query an entity's expense and revenue transactions for the given fiscal 
  # years.
  #
  # Arguments:
  #   t_id (num): The entity's Transparency ID, as queried from Salesforce
  #     rather than Transparency.
  #   fy_1 (num): The first fiscal year to query, as requested by the U.S.
  #     Census Bureau.
  #   fy_2 (num): The second fiscal year to query, as requested by the U.S.
  #     Census Bureau.
  #
  # Value:
  #   Tibble.
  
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT 
            fiscal_year,
            type AS transaction_type,
            amount,
            description,
            org1, org2, org3, org4
            cat1, cat2, cat3, cat4,
            fund1, fund2,
            account_number
          FROM transaction
          WHERE batch_id IN (
            SELECT id
            FROM batch
            WHERE entity_id = ", t_id, "
            AND status IN ('PROCESSED', 'PROCESSING', 'DONTDELETE'))
          AND type IN (1, 2)
          AND fiscal_year IN (", fy_1, ",", fy_2, ")")) %>% 
    as_tibble() %>% 
    mutate(t_id = t_id)
}
```

## `write_file`

```{r}
write_file <- function(report_name, csv_name, fy_1, fy_2) {
  # Export a .csv version of a tibble.
  #
  # Arguments:
  #   report_name (tibble): The name of the tibble to export.
  #   csv_name (char): The name of the .csv file.
  #   
  
  file_name <- paste0("~/utah_", fy_1, "_", fy_2, "_")
  
  write_csv(
    report_name, 
    paste0(
      file_name, csv_name, ".csv"))
}
```

# Execution

```{r}
active_govts <- 
  dbGetQuery(
    odbc_sf,
    "SELECT 
      a.Transparency_ID__c AS t_id
    FROM Account AS a
    LEFT JOIN RecordType AS r
    ON a.RecordTypeId = r.Id
    WHERE a.RecordTypeId IN (
      SELECT Id
      FROM RecordType
      WHERE SobjectType = 'Account'
      AND IsActive = 'TRUE'
      AND Name IN (
        'City',
        'County',
        'Interlocal',
        'Local and Special Service District',
        'Town'))
    AND a.Name <> 'test city 2'
    AND Entity_Status__c NOT IN ('Inactive', 'Dissolved')") %>% 
  as_tibble() %>% 
  filter(!is.na(t_id)) %>% 
  mutate(
    entity_name    = map_chr(t_id, query_entity_table, "name"),
    govt_lvl       = map_chr(t_id, query_entity_table, "govt_lvl"),
    fy_begin_month = map_chr(t_id, query_entity_table, "fiscal_period"))
```

```{r}
# I don't know why, but I occasionally get an error message when running the
# code to create the reports for counties and cities and towns. Running the 
# code again, however, usually solves the problem.

report_counties <- 
  create_govt_lvl_report(active_govts, "COUNTY", fy_1, fy_2)

report_cities_and_towns <- 
  create_govt_lvl_report(active_govts, "CITY", fy_1, fy_2)

report_interlocals <- 
  create_govt_lvl_report(active_govts, "INTERLOCAL", fy_1, fy_2)

report_local_districts <- 
  create_govt_lvl_report(active_govts, "LOCAL DISTRICTS", fy_1, fy_2)

report_service_districts <- 
  create_govt_lvl_report(active_govts, "SERVICE DISTRICTS", fy_1, fy_2)
```

## Export

```{r}
active_govts %>% 
  rename(entity_id = t_id) %>% 
  write_file("entity_information", fy_1, fy_2)

report_counties %>%  
  write_file("county", fy_1, fy_2)

report_cities_and_towns %>% 
  write_file("city", fy_1, fy_2)

report_interlocals %>% 
  write_file("interlocal", fy_1, fy_2)

report_local_districts %>%  
  write_file("local", fy_1, fy_2)

report_service_districts %>%  
  write_file("service", fy_1, fy_2)

dbGetQuery(
  odbc_aws,
  "SELECT id, name FROM transaction_group") %>% 
  write_file("id_crosswalk_transactions", fy_1, fy_2)
```

If `report_cities_and_towns` is too large to send via email:

```{r, eval=FALSE}
report_cities_and_towns %>% 
  slice(1:2500000) %>% 
  write_file("city_1", fy_1, fy_2)

report_cities_and_towns %>% 
  slice(2500001:5000000) %>% 
  write_file("city_2", fy_1, fy_2)

report_cities_and_towns %>% 
  slice(5000001:7500000) %>% 
  write_file("city_3", fy_1, fy_2)

report_cities_and_towns %>% 
  slice(7500001:nrow(report_cities_and_towns)) %>% 
  write_file("city_4", fy_1, fy_2)
```

# DBMS Disconnection

```{r}
dbDisconnect(odbc_aws)
```