---
title: "The State of Utah and Utah Interactive"
author: "Michael Jensen"
date: "December 2018"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---
***
# Program Description

What does the Transparency data tell us about the financial relationship between the State of Utah and Utah Interactive. In particular,

* How much does the State of Utah pay Utah Interactive?
* In which direction does money flow between the State of Utah and Utah Interactive?
* Does Utah Interactive have more than one contract with the State of Utah?
* Which sub-organizations of the State of Utah have the greatest financial relationship with Utah Interactive?

# Program

## Inputs, Packages, & Data Connections

```{r}
library(knitr)
library(odbc)
library(scales)
library(stringr)
library(tidyverse)

odbc_aws <- dbConnect(odbc::odbc(), "transpAWS")
odbc_dw  <- dbConnect(odbc::odbc(), "StateDW", password = "DW1234")
```

## Transparency

### Vendor IDs

```{sql, connection=odbc_aws, output.var=aws_vendor_is_ui}
SELECT
  vendor.id   AS vendor_id,
  vendor.name AS vendor_name
FROM vendor
JOIN entity
ON vendor.entity_id = entity.id
WHERE (
  vendor.name LIKE "%utah interactive%" OR
  vendor.name LIKE "ui%")
AND  (
  vendor.name NOT LIKE "uinta%"  AND
  vendor.name NOT LIKE "uia%"    AND
  vendor.name NOT LIKE "uil%"    AND
  vendor.name NOT LIKE "uip%"    AND
  vendor.name NOT LIKE "uis%inc" AND
  vendor.name NOT LIKE "uit%")
AND entity_id = 1
```

The following have some tie to Utah Interactive (e.g., appear in the State's contract with Utah Interactive as a related entity or referenced service) and may appear as a vendor name (my purpose here is to cast a wide net and see what appears in the Transparency data):

* NIC Inc. (Utah Interactive is a subsidiary)
* Chase Bank
* GovPay
* Portal Revenue Account
* StateDX
* Richard Olsen (his name appears on UI's contract with the State)

```{sql, connection=odbc_aws, output.var=aws_vendor_is_other}
SELECT
  vendor.id   AS vendor_id,
  vendor.name AS vendor_name
FROM vendor
JOIN entity 
ON vendor.entity_id = entity.id
WHERE (
  vendor.name LIKE "%nic inc%"                 OR
  vendor.name LIKE "%nicusa%"                  OR
  vendor.name LIKE "%nic usa%"                 OR
  vendor.name LIKE "%nic electronic services%" OR
  vendor.name LIKE "%egov%"                    OR
  vendor.name LIKE "%chase bank%"              OR
  vendor.name LIKE "%chase payment services%"  OR
  vendor.name LIKE "%govpay%"                  OR
  vendor.name LIKE "%richard olsen%"           OR
  vendor.name LIKE "%portal%"                  OR
  vendor.name LIKE "%statedx%")
AND (
  vendor.name NOT LIKE "%clinic inc%"    AND
  vendor.name NOT LIKE "%carbonic inc"   AND
  vendor.name NOT LIKE "%electronic inc" AND
  vendor.name NOT LIKE "environic inc"   AND
  vendor.name NOT LIKE "ferhatbegovic%"  AND
  vendor.name NOT LIKE "%mechanic inc")
AND entity_id = 1
```

```{r}
aws_vendor_is_ui <- 
  aws_vendor_is_ui %>% 
  as_tibble()

aws_vendor_is_other <- 
  aws_vendor_is_other %>% 
  as_tibble()

aws_vendor_is_ui$vendor_id <- 
  as.character(aws_vendor_is_ui$vendor_id)

aws_vendor_is_other$vendor_id <- 
  as.character(aws_vendor_is_other$vendor_id)

vendor_ids <- 
  list(aws_vendor_is_ui    = aws_vendor_is_ui,
       aws_vendor_is_other = aws_vendor_is_other)

rm(aws_vendor_is_ui, aws_vendor_is_other)
```

### Vendor Summary Table

```{r}
query_vendor_summary_table <- function(vendor_id) {
  # Arguments:
  # - vendor_id: The vendor ID.
  
  # Returns:
  # A tibble containing the queried information from the Summary Table for the
  # specified vendor.
  
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT vendor_id, fiscal_year, type, total
          FROM vendor_summary
          WHERE vendor_id = ", vendor_id, "
          AND type <> 5")) %>% 
    as_tibble()
}

vendor_summary_table_info <- list()

vendor_summary_table_info[["ui"]] <- 
  vendor_ids[["aws_vendor_is_ui"]] %>% 
  .$vendor_id %>% 
  map(query_vendor_summary_table) %>% 
  bind_rows() %>% 
  mutate(vendor_id = as.character(vendor_id)) %>% 
  left_join(vendor_ids[["aws_vendor_is_ui"]], by = "vendor_id") %>% 
  select(vendor_name, vendor_id, fiscal_year, type, total)

vendor_summary_table_info[["other"]] <- 
  vendor_ids[["aws_vendor_is_other"]] %>% 
  .$vendor_id %>% 
  map(query_vendor_summary_table) %>% 
  bind_rows() %>% 
  mutate(vendor_id = as.character(vendor_id)) %>% 
  left_join(vendor_ids[["aws_vendor_is_other"]], by = "vendor_id") %>% 
  select(vendor_name, vendor_id, fiscal_year, type, total)

vendor_summary_table_info[["year_by_year_ui"]] <- 
  vendor_summary_table_info[["ui"]] %>% 
  group_by(fiscal_year) %>% 
  summarize(total = sum(total)) %>% 
  mutate(total = dollar(total))

vendor_summary_table_info[["year_by_year_other"]] <- 
  vendor_summary_table_info[["other"]] %>% 
  group_by(vendor_name, fiscal_year) %>% 
  summarize(total = sum(total)) %>% 
  mutate(total = dollar(total))

vendor_summary_table_info[["total_ui"]] <- 
  vendor_summary_table_info[["ui"]] %>% 
  summarize(total = sum(total)) %>% 
  mutate(total = dollar(total))
  
vendor_summary_table_info[["total_other"]] <- 
  vendor_summary_table_info[["other"]] %>% 
  group_by(vendor_name) %>% 
  summarize(total = sum(total)) %>% 
  mutate(total = dollar(total))

rm(query_vendor_summary_table)
```

### Transaction Tables

```{r, message=FALSE}
query_transaction_table <- function(vendor_id, table_name) {
  # Arguments:
  # - vendor_id: The vendor ID.
  # - table_name: The name of the transaction table (e.g., transaction,
  #   transaction_2009, transaction_2013).
  
  # Returns:
  # A tibble containing the queried transaction information from the specified
  # Transaction Table for the specified vendor.
  
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT vendor_id, fiscal_year, posting_date, type, amount, 
                 description, contract_name, contract_number, org1, org2, org3,
                 cat1, cat2, cat3, fund1, fund2
          FROM ", table_name, "
          WHERE vendor_id = ", vendor_id, "
          AND type <> 5")) %>% 
    as_tibble()
}

transaction_group_table <- 
  dbGetQuery(
    odbc_aws,
    "SELECT id, name FROM transaction_group")

transaction_group_table$id <- 
  as.character(transaction_group_table$id)

transaction_table_for_ui <- 
  list(
    transaction = 
    map(vendor_ids[["aws_vendor_is_ui"]]$vendor_id,
        query_transaction_table,
        table_name = "transaction") %>% 
    bind_rows(),
    
    transaction_2009 = 
      map(vendor_ids[["aws_vendor_is_ui"]]$vendor_id,
          query_transaction_table,
          table_name = "transaction_2009") %>% 
      bind_rows(),
    
    transaction_2010 = 
      map(vendor_ids[["aws_vendor_is_ui"]]$vendor_id,
          query_transaction_table,
          table_name = "transaction_2010") %>% 
      bind_rows(),
    
    transaction_2011 = 
      map(vendor_ids[["aws_vendor_is_ui"]]$vendor_id,
          query_transaction_table,
          table_name = "transaction_2011") %>% 
      bind_rows(),
    
    transaction_2012 = 
      map(vendor_ids[["aws_vendor_is_ui"]]$vendor_id,
          query_transaction_table,
          table_name = "transaction_2012") %>% 
      bind_rows(),
    
    transaction_2013 = 
      map(vendor_ids[["aws_vendor_is_ui"]]$vendor_id,
          query_transaction_table,
          table_name = "transaction_2013") %>% 
      bind_rows()) %>% 
  bind_rows() %>% 
  mutate(vendor_id   = as.character(vendor_id),
         fiscal_year = as.character(fiscal_year),
         org1        = as.character(org1),
         org2        = as.character(org2),
         org3        = as.character(org3),
         cat1        = as.character(cat1),
         cat2        = as.character(cat2),
         cat3        = as.character(cat3),
         fund1       = as.character(fund1),
         fund2       = as.character(fund2)) %>% 
  left_join(vendor_ids[["aws_vendor_is_ui"]])

transaction_table_for_ui <- 
  transaction_table_for_ui %>% 
  left_join(transaction_group_table,
            by = c("org1" = "id")) %>% 
  select(-"org1") %>% 
  rename("org1" = "name")

transaction_table_for_ui <- 
  transaction_table_for_ui %>% 
  left_join(transaction_group_table,
            by = c("org2" = "id")) %>% 
  select(-"org2") %>% 
  rename("org2" = "name")

transaction_table_for_ui <- 
  transaction_table_for_ui %>% 
  left_join(transaction_group_table,
            by = c("org3" = "id")) %>% 
  select(-"org3") %>% 
  rename("org3" = "name")

transaction_table_for_ui <- 
  transaction_table_for_ui %>% 
  left_join(transaction_group_table,
            by = c("cat1" = "id")) %>% 
  select(-"cat1") %>% 
  rename("cat1" = "name")

transaction_table_for_ui <- 
  transaction_table_for_ui %>% 
  left_join(transaction_group_table,
            by = c("cat2" = "id")) %>% 
  select(-"cat2") %>% 
  rename("cat2" = "name")

transaction_table_for_ui <- 
  transaction_table_for_ui %>% 
  left_join(transaction_group_table,
            by = c("cat3" = "id")) %>% 
  select(-"cat3") %>% 
  rename("cat3" = "name")

transaction_table_for_ui <- 
  transaction_table_for_ui %>% 
  left_join(transaction_group_table,
            by = c("fund1" = "id")) %>% 
  select(-"fund1") %>% 
  rename("fund1" = "name")

transaction_table_for_ui <- 
  transaction_table_for_ui %>% 
  left_join(transaction_group_table,
            by = c("fund2" = "id")) %>% 
  select(-"fund2") %>% 
  rename("fund2" = "name")

transaction_table_for_ui <- 
  transaction_table_for_ui %>% 
  select(vendor_name, vendor_id, fiscal_year, posting_date, type, amount,
         description, contract_name, contract_number, org1, org2, org3, 
         cat1, cat2, cat3, fund1, fund2)

transaction_table_for_other <- 
  list(
    transaction = 
    map(vendor_ids[["aws_vendor_is_other"]]$vendor_id,
        query_transaction_table,
        table_name = "transaction") %>% 
    bind_rows(),
    
    transaction_2009 = 
      map(vendor_ids[["aws_vendor_is_other"]]$vendor_id,
          query_transaction_table,
          table_name = "transaction_2009") %>% 
      bind_rows(),
    
    transaction_2010 = 
      map(vendor_ids[["aws_vendor_is_other"]]$vendor_id,
          query_transaction_table,
          table_name = "transaction_2010") %>% 
      bind_rows(),
    
    transaction_2011 = 
      map(vendor_ids[["aws_vendor_is_other"]]$vendor_id,
          query_transaction_table,
          table_name = "transaction_2011") %>% 
      bind_rows(),
    
    transaction_2012 = 
      map(vendor_ids[["aws_vendor_is_other"]]$vendor_id,
          query_transaction_table,
          table_name = "transaction_2012") %>% 
      bind_rows(),
    
    transaction_2013 = 
      map(vendor_ids[["aws_vendor_is_other"]]$vendor_id,
          query_transaction_table,
          table_name = "transaction_2013") %>% 
      bind_rows()) %>% 
  bind_rows() %>% 
  mutate(vendor_id   = as.character(vendor_id),
         fiscal_year = as.character(fiscal_year),
         org1        = as.character(org1),
         org2        = as.character(org2),
         org3        = as.character(org3),
         cat1        = as.character(cat1),
         cat2        = as.character(cat2),
         cat3        = as.character(cat3),
         fund1       = as.character(fund1),
         fund2       = as.character(fund2)) %>% 
  left_join(vendor_ids[["aws_vendor_is_other"]],
            by = "vendor_id")

transaction_table_for_other <- 
  transaction_table_for_other %>% 
  left_join(transaction_group_table,
            by = c("org1" = "id")) %>% 
  select(-"org1") %>% 
  rename("org1" = "name")

transaction_table_for_other <- 
  transaction_table_for_other %>% 
  left_join(transaction_group_table,
            by = c("org2" = "id")) %>% 
  select(-"org2") %>% 
  rename("org2" = "name")

transaction_table_for_other <- 
  transaction_table_for_other %>% 
  left_join(transaction_group_table,
            by = c("org3" = "id")) %>% 
  select(-"org3") %>% 
  rename("org3" = "name")

transaction_table_for_other <- 
  transaction_table_for_other %>% 
  left_join(transaction_group_table,
            by = c("cat1" = "id")) %>% 
  select(-"cat1") %>% 
  rename("cat1" = "name")

transaction_table_for_other <- 
  transaction_table_for_other %>% 
  left_join(transaction_group_table,
            by = c("cat2" = "id")) %>% 
  select(-"cat2") %>% 
  rename("cat2" = "name")

transaction_table_for_other <- 
  transaction_table_for_other %>% 
  left_join(transaction_group_table,
            by = c("cat3" = "id")) %>% 
  select(-"cat3") %>% 
  rename("cat3" = "name")

transaction_table_for_other <- 
  transaction_table_for_other %>% 
  left_join(transaction_group_table,
            by = c("fund1" = "id")) %>% 
  select(-"fund1") %>% 
  rename("fund1" = "name")

transaction_table_for_other <- 
  transaction_table_for_other %>% 
  left_join(transaction_group_table,
            by = c("fund2" = "id")) %>% 
  select(-"fund2") %>% 
  rename("fund2" = "name")

transaction_table_for_other <- 
  transaction_table_for_other %>% 
  select(vendor_name, vendor_id, fiscal_year, posting_date, type, amount,
         description, contract_name, contract_number, org1, org2, org3, 
         cat1, cat2, cat3, fund1, fund2)

transaction_table_info <- 
  list(ui    = transaction_table_for_ui,
       other = transaction_table_for_other)

rm(transaction_table_for_ui, transaction_table_for_other, transaction_group_table)

transaction_table_info[["year_by_year_ui"]] <- 
  transaction_table_info[["ui"]] %>% 
  group_by(fiscal_year) %>% 
  summarize(total = sum(amount)) %>% 
  mutate(total = dollar(total))

transaction_table_info[["year_by_year_other"]] <- 
  transaction_table_info[["other"]] %>% 
  group_by(vendor_name, fiscal_year) %>% 
  summarize(total = sum(amount)) %>% 
  mutate(total = dollar(total))

transaction_table_info[["total_ui"]] <- 
  transaction_table_info[["ui"]] %>% 
  summarize(total = sum(amount)) %>% 
  mutate(total = dollar(total))

transaction_table_info[["total_other"]] <- 
  transaction_table_info[["other"]] %>% 
  group_by(vendor_name) %>% 
  summarize(total = sum(amount)) %>% 
  mutate(total = dollar(total))

transaction_table_info[["by_org_3_ui"]] <- 
  transaction_table_info[["ui"]] %>% 
  group_by(org1, org2, org3) %>% 
  summarize(total = sum(amount)) %>% 
  arrange(desc(total)) %>% 
  mutate(total = dollar(total))

transaction_table_info[["distinct_contract_names_and_ids_ui"]] <- 
  transaction_table_info[["ui"]] %>% 
  distinct(vendor_name, vendor_id)

transaction_table_info[["transaction_descriptions_ui"]] <- 
  transaction_table_info[["ui"]] %>% 
  distinct(description) %>% 
  arrange(description)

transaction_table_info[["transaction_descriptions_other"]] <- 
  transaction_table_info[["other"]] %>% 
  distinct(description) %>% 
  arrange(description)

rm(query_transaction_table)
```

## StateDW

### Vendor IDS

*Note: Using the Adaptive Server Enterprise ODBC to select a table from State Data Warehouse (StateDW) requires calling the table as <database>.<owner>.<object_name>.<column_name>. Use "sp_help" to identify the owner:*

```{r}
sp_help <- 
  dbGetQuery(
    odbc_dw,
    "sp_help")
```

```{sql, connection=odbc_dw, output.var=dw_vendor_is_ui}
SELECT 
  Vendor_Customer AS vendor_id, 
  Legal_Name      AS vendor_name
FROM StateDW.dbo.Vendor_Customer
WHERE (
  LOWER(Legal_Name) LIKE "%utah interactive%" OR
  LOWER(Legal_Name) LIKE "ui%")
AND (
  LOWER(Legal_Name) NOT LIKE "uint%"   AND
  LOWER(Legal_Name) NOT LIKE "uil%"    AND
  LOWER(Legal_Name) NOT LIKE "uin%"    AND
  LOWER(Legal_Name) NOT LIKE "uis%"    AND
  LOWER(Legal_Name) NOT LIKE "uit%")
```

```{sql, connection=odbc_dw, output.var=dw_vendor_is_other}
SELECT 
  Vendor_Customer AS vendor_id, 
  Legal_Name      AS vendor_name
FROM StateDW.dbo.Vendor_Customer
WHERE (
  LOWER(Legal_Name) LIKE "%nic inc%"                 OR
  LOWER(Legal_Name) LIKE "%nicusa%"                  OR
  LOWER(Legal_Name) LIKE "%nic usa%"                 OR
  LOWER(Legal_Name) LIKE "%nic electronic services%" OR
  LOWER(Legal_Name) LIKE "%egov%"                    OR
  LOWER(Legal_Name) LIKE "%chase bank%"              OR
  LOWER(Legal_Name) LIKE "%chase payment services%"  OR
  LOWER(Legal_Name) LIKE "%govpay%"                  OR
  LOWER(Legal_Name) LIKE "%richard olsen%"           OR
  LOWER(Legal_Name) LIKE "%portal%"                  OR
  LOWER(Legal_Name) LIKE "%statedx%")
AND (
  LOWER(Legal_Name) NOT LIKE "benito segovia"   AND
  LOWER(Legal_Name) NOT LIKE "ciara gregovich"  AND
  LOWER(Legal_Name) NOT LIKE "%clinic inc%"     AND
  LOWER(Legal_Name) NOT LIKE "%cliinic inc%"    AND
  LOWER(Legal_Name) NOT LIKE "%carbonic inc%"   AND
  LOWER(Legal_Name) NOT LIKE "%electronic inc%" AND
  LOWER(Legal_Name) NOT LIKE "emina alibegovic" AND
  LOWER(Legal_Name) NOT LIKE "environic inc%"   AND
  LOWER(Legal_Name) NOT LIKE "%mechanic inc%"   AND
  LOWER(Legal_Name) NOT LIKE "segovia inc%")
```

```{r}
dw_vendor_is_ui <- 
  dw_vendor_is_ui %>% 
  as_tibble()

dw_vendor_is_other <- 
  dw_vendor_is_other %>% 
  as_tibble()

vendor_ids[["dw_vendor_is_ui"]]    <- dw_vendor_is_ui
vendor_ids[["dw_vendor_is_other"]] <- dw_vendor_is_other

rm(dw_vendor_is_ui, dw_vendor_is_other)
```

### Accounting Journal Table

#### All UI-related Transactions

```{sql, connection=odbc_dw, output.var=aj_table_ui}
SELECT 
  Vendor_Customer_Name, 
  Vendor_Customer,
  Fiscal_Year, 
  Amount, 
  Department,
  Division,
  Line_Description, 
  Account_Type
FROM StateDW.dbo.Accounting_Journal
WHERE Vendor_Customer IN (
  SELECT 
    Vendor_Customer AS vendor_id
  FROM StateDW.dbo.Vendor_Customer
  WHERE (
    LOWER(Legal_Name) LIKE "%utah interactive%" OR
    LOWER(Legal_Name) LIKE "ui%")
  AND (
    LOWER(Legal_Name) NOT LIKE "uint%"   AND
    LOWER(Legal_Name) NOT LIKE "uil%"    AND
    LOWER(Legal_Name) NOT LIKE "uin%"    AND
    LOWER(Legal_Name) NOT LIKE "uis%"    AND
    LOWER(Legal_Name) NOT LIKE "uit%"))
```

```{sql, connection=odbc_dw, output.var=department_table}
SELECT Department, Department_Name
FROM Department
```

```{r}
aj_table_ui <- 
  aj_table_ui %>% 
  as_tibble()

department_table <- 
  department_table %>% 
  as_tibble()

department_table$Department <- 
  department_table$Department %>% 
  str_trim(side = "right")

aj_table_ui <- 
  aj_table_ui %>%
  left_join(department_table,
            by = "Department") %>% 
  select(-Department)

rm(department_table)

aj_table_info <- 
  list(ui = aj_table_ui)

rm(aj_table_ui)
```

#### Expenditures

```{r}
aj_table_info[["exp_year_by_year"]] <- 
  aj_table_info[["ui"]] %>% 
  filter(Account_Type == "22") %>% 
  group_by(Fiscal_Year) %>% 
  summarize(total = sum(Amount)) %>% 
  mutate(total = dollar(total))

aj_table_info[["exp_total_ui"]] <- 
  aj_table_info[["ui"]] %>% 
  filter(Account_Type == "22") %>% 
  summarize(total = sum(Amount)) %>% 
  mutate(total = dollar(total))

aj_table_info[["exp_by_department"]] <- 
  aj_table_info[["ui"]] %>% 
  filter(Account_Type == "22") %>% 
  group_by(Department_Name) %>% 
  summarize(total = sum(Amount)) %>% 
  arrange(desc(total)) %>% 
  mutate(total = dollar(total))

aj_table_info[["exp_line_descriptions"]] <- 
  aj_table_info[["ui"]] %>% 
  filter(Account_Type == "22") %>% 
  distinct(Line_Description)

aj_table_info[["exp_vendor_names"]] <- 
  aj_table_info[["ui"]] %>% 
  filter(Account_Type == "22") %>% 
  distinct(Vendor_Customer_Name, Vendor_Customer)
```

#### Revenues

```{r}
aj_table_info[["rev_year_by_year"]] <- 
  aj_table_info[["ui"]] %>% 
  filter(Account_Type == "31") %>% 
  group_by(Fiscal_Year) %>% 
  summarize(total = sum(Amount)) %>% 
  mutate(total = dollar(total))

aj_table_info[["rev_total_ui"]] <- 
  aj_table_info[["ui"]] %>% 
  filter(Account_Type == "31") %>% 
  summarize(total = sum(Amount)) %>% 
  mutate(total = dollar(total))

aj_table_info[["rev_by_department"]] <- 
  aj_table_info[["ui"]] %>% 
  filter(Account_Type == "31") %>% 
  group_by(Department_Name) %>% 
  summarize(total = sum(Amount)) %>% 
  arrange(desc(total)) %>% 
  mutate(total = dollar(total))

aj_table_info[["rev_line_descriptions"]] <- 
  aj_table_info[["ui"]] %>% 
  filter(Account_Type == "31") %>% 
  distinct(Line_Description)

aj_table_info[["rev_vendor_names"]] <- 
  aj_table_info[["ui"]] %>% 
  filter(Account_Type == "31") %>% 
  distinct(Vendor_Customer_Name, Vendor_Customer)
```

## Export

```{r}
transaction_table_info[["ui"]] %>% 
  write_csv("C:/Users/mjensen1/Desktop/Transaction Table UI.csv")

transaction_table_info[["other"]] %>% 
  write_csv("C:/Users/mjensen1/Desktop/Transaction Table Other.csv")

transaction_table_info[["year_by_year_ui"]] %>% 
  write_csv("C:/Users/mjensen1/Desktop/Transaction Table Year by Year UI.csv")

transaction_table_info[["year_by_year_other"]] %>% 
  write_csv("C:/Users/mjensen1/Desktop/Transaction Table Year by Year Other.csv")

transaction_table_info[["total_ui"]] %>% 
  write_csv("C:/Users/mjensen1/Desktop/Transaction Table Total UI.csv")

transaction_table_info[["total_other"]] %>% 
  write_csv("C:/Users/mjensen1/Desktop/Transaction Table Total Other.csv")

transaction_table_info[["by_org_3_ui"]] %>% 
  write_csv("C:/Users/mjensen1/Desktop/Transaction Table By Org UI.csv")

transaction_table_info[["distinct_contract_names_and_ids_ui"]] %>% 
  write_csv("C:/Users/mjensen1/Desktop/Transaction Table Contract Names and IDs UI.csv")

transaction_table_info[["transaction_descriptions_ui"]] %>% 
  write_csv("C:/Users/mjensen1/Desktop/Transaction Table Descriptions UI.csv")

transaction_table_info[["transaction_descriptions_other"]] %>% 
  write_csv("C:/Users/mjensen1/Desktop/Transaction Table Descriptions Other.csv")

aj_table_info[["ui"]] %>% 
  write_csv("C:/Users/mjensen1/Desktop/FINET UI.csv")

aj_table_info[["rev_year_by_year"]] %>% 
  write_csv("C:/Users/mjensen1/Desktop/FINET Revenue from UI.csv")
```

## Close

```{r}
dbDisconnect(odbc_aws, odbc_dw)
rm(list = ls())
```