---
title: "Browse AWS 2.1"
author: "Michael Jensen"
date: "July 2018"
output: html_notebook
---
# Program Description

Browse AWS for entity-specific and database-wide information.

# Program

## Inputs, Packages, & Data Connections

```{r}
library(odbc)

odbc_aws <- dbConnect(odbc::odbc(), "transpAWS")
```

## Entity-specific Data

### Entity Transparency ID

Browse entity names and IDs:

```{sql, connection = odbc_aws, output.var = "names_and_ids"}
SELECT name, id
FROM entity
```

Assign the Transparency ID:

```{r}
t_id <- 623
```

```{sql, connection = odbc_aws, output.var = "t_id1"}
set @t_id1 := '623'
```


```{sql, connection = odbc_aws, output.var = "test"}
SELECT name
FROM entity
WHERE entity_id = @t_id1
```


```{r}
names_and_ids <- 
  odbc_aws %>%
  dbGetQuery(
    paste("
          SELECT name, id
          FROM entity"))
```

### Entity Table

```{r}
entity_table <- 
  odbc_aws %>% 
  dbGetQuery(
    paste("
          SELECT name, id, govt_lvl, fiscal_period, payroll_period
          FROM entity
          WHERE id = ", transparency_id))
```

### Batch Table

```{r}
batch_table <- 
  odbc_aws %>% 
  dbGetQuery(
    paste("
          SELECT id, begin_txn_date, end_txn_date, upload_username,
                 upload_date, processed_date, status, status_message
          FROM batch
          WHERE entity_id = ", transparency_id))
```

### Transaction Table

```{r}
all_transactions <- 
  odbc_aws %>% 
  dbGetQuery(
    paste("
          SELECT *
          FROM transaction
          WHERE batch_id = 52950"))
```

```{sql, connection = odbc_aws, output.var = "bad_batches"}
SELECT COUNT(*)
FROM transaction
WHERE batch_id IN (
SELECT id FROM batch WHERE status IN ('DELETED'))
```

#### Expenses

```{r}
expenses <- 
  odbc_aws %>% 
  dbGetQuery(
    paste("
          SELECT id, posting_date, amount, fiscal_year
          FROM transaction
          WHERE batch_id IN (
            SELECT id
            FROM batch
            WHERE entity_id = ", transparency_id, "
            AND status IN ('PROCESSED', 'PROCESSING'))
          AND type = 1"))
```

#### Revenue

```{r}
revenues <- 
  odbc_aws %>% 
  dbGetQuery(
    paste("
          SELECT id, posting_date, amount, fiscal_year
          FROM transaction
          WHERE batch_id IN (
            SELECT id
            FROM batch
            WHERE entity_id = ", transparency_id, "
            AND status IN ('PROCESSED', 'PROCESSING'))
          AND type = 2"))
```

#### W-2 Employee Compensation

```{r}
w2_comp <- 
  odbc_aws %>% 
  dbGetQuery(
    paste("
          SELECT id, posting_date, amount, fiscal_year
          FROM transaction
          WHERE batch_id IN (
            SELECT id
            FROM batch
            WHERE entity_id = ", transparency_id, "
            AND status IN ('PROCESSED', 'PROCESSING'))
          AND type = 3"))
```

### Vendor Table

```{sql, connection = odbc_aws, output.var = "vendor_table"}
SELECT name
FROM vendor
```

## Size of the database

```{sql, connection = odbc_aws, output.var = "size"}
select table_schema as 'Database', table_name as 'Table', 
round(((data_length + index_length) / 1024 / 1024), 2) 'Size in MB'
FROM information_schema.TABLES
ORDER BY (data_length + index_length) DESC
```

```{r}
sum(size$`Size in MB`)
```

## AWS Data

### Record Counts

Overall: 

```{r}
aws_table_status <- 
  dbGetQuery(
    odbc_aws,
    paste("
          SHOW TABLE STATUS"))

row_count <- sum(aws_table_status$Rows)
```

Per table:
* Note there is a discrepancy between what is reported overall and what is reported per table. I don't know why the discrepancy exists.

```{r}
entity_count <- 
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT COUNT(*) FROM entity"))

batch_count <- 
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT COUNT(*) FROM batch"))

transaction_count <- 
  dbGetQuery(
    odbc_aws,
    paste("
          SELECT COUNT(*) FROM transaction"))
```

```{sql, connection = odbc_aws, output.var = "stuff"}
select * from transaction where batch_id = 44169
```

```{sql, connection = odbc_aws, output.var = "index1"}
show index from transaction
```

```{sql, connection = odbc_aws, output.var = "index2"}
show index from batch
```

```{sql, connection = odbc_aws, output.var = "index3"}
show index from entity
```

```{sql, connection = odbc_aws, output.var = "create_index"}
CREATE INDEX transaction_batchid
ON transaction (batch_id)
```


```{sql, connection = odbc_aws, output.var = "stuff"}
SELECT DISTINCT posting_date
FROM transaction
WHERE batch_id IN (
  SELECT id
  FROM batch
  WHERE entity_id = 259
  AND status IN ('PROCESSED', 'PROCESSING'))
AND type = 1
AND fiscal_year > 2013
AND YEAR(posting_date) = fiscal_year
```

```{sql, connection = odbc_aws, output.var = "stuff2"}
EXPLAIN SELECT DISTINCT posting_date
FROM transaction
WHERE batch_id IN (
  SELECT id
  FROM batch
  WHERE entity_id = 259
  AND status IN ('PROCESSED', 'PROCESSING'))
AND type = 1
AND fiscal_year > 2013
AND YEAR(posting_date) = fiscal_year
```

```{r}
stuff2 %>% 
  write.csv(
    file = "C:/Users/mjensen1/Documents/stuff2.csv",
    row.names = FALSE)
```


## Close

```{r}
dbDisconnect(odbc_aws)
rm(list = ls())
```